---
title: "Turbine Collision Risk: Exploration Circular Distributions and Acoustic Monitoring Area"
description: ""
author:
    - name: "Cédric Scherer"
      url: https://cedricscherer.com
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://www.izw-berlin.de/en/home.html
      orcid_id: 0000-0003-0645-5666
    - name: "Christian Voigt"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://www.izw-berlin.de/en/home.html
      orcid_id: 0000-0002-0706-3974
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate
        code_folding: true  
        toc: true            
        toc_depth: 2         
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 15, fig.height = 10, 
                      dev = "ragg_png", res = 1000, retina = 1)
```

## Preparation 

```{r prep}
library(tidyverse)
library(ggtext)
library(spatstat.core)
library(patchwork)

theme_set(theme_light(base_size = 10, base_family = "Open Sans"))
theme_update(
  panel.grid.major = element_line(size = .3),
  panel.grid.minor = element_blank(),
  plot.title = element_markdown(size = 18),
  plot.title.position = "plot",
  plot.margin = margin(rep(25, 4))
)
```

## Research Question

* Predictive power of the acoustic monitoring

> Is the predictive power of the current acoustic monitoring sufficient enough to estimate the true number of killed bats?

### Predictions

The predictive power of the acoustic monitoring for the extrapolation of the expected number of stroke victims is decreasing

* in case the crossing bats are not distributed uniformly or randomly.

* with increasing length of the rotor blades.

* for species with high-frequency echo calls.


### Open Questions

* wie die Dichte skalieren zwischen großen und kleinen Windrädern? 
  - z.B. von innen nach außen abhängig von relativer oder absoluter Distanz zum Mittelpunkt?
  
* globale oder lokale Anzahl an Fledermäusen konstant halten?

## Inputs

We have the following parameters we can vary:

* length of rotor blades (`radius_rotor`) - 60 m versus 33 m
  + determines area of wind turbine (`area_rotor` as `pi * radius_rotor^2`)
* proportion of area covered by acoustic monitoring (`proportion_covered`)
  + determines area of acoustic monitoring (`area_monitored` as `area_rotor * proportion_covered`)
  + determines radius to detect bars (`radius_monitored` as `sqrt(area_monitored / pi)`)
* number of bats simulated (`n`)
  + could be either total (for now) or number monitored (maybe later)

```{r input-prep}
## radius circle (~ length rotor blades)
radius_rotor <- 1 

## % area covered by acoustic monitoring
proportion_covered <- .05 

## radius acoustic monitoring via % area covered + length rotor blades
area_rotor <- pi * radius_rotor^2
area_monitored <- area_rotor * proportion_covered
radius_monitored <- sqrt(area_monitored / pi)

## mask for window
circle <- disc(
  radius = radius_rotor, 
  centre = c(0, 0), 
  mask = FALSE, 
  npoly = 5000
)

## number of points (~ bats)
n <- 500
```

## Circular Distributions

### Generate Point Patterns

```{r point-pattern-generation}
## source sunflower function for uniform distributions
source(here::here("R", "src", "generate-distributions.R"))

## fix random number genreration to ensure reproducibility
set.seed(12345)

## random
pp_rand <- spatstat.core::rpoint(n, win = circle)
df_rand <- as.data.frame(pp_rand) %>% mutate(dist = x^2 + y^2)


## uniform
pp_unif <- spatstat.core::runifpoint(n, win = circle)
df_unif <- as.data.frame(pp_unif) %>% mutate(dist = x^2 + y^2)

df_sunf <- sunflower(n, 1, 'planar') %>% mutate(dist = x^2 + y^2)


## directional: inner > outer
pp_inn <- rpoint(n, function(x,y) {1 - (abs(-x^2 - y^2)) + .01}, win = circle)
df_inn <- as.data.frame(pp_inn) %>% mutate(dist = x^2 + y^2)


## directional: outer > inner
pp_out <- rpoint(n, function(x,y) {(abs(x^2 + y^2)) + .01}, win = circle)
df_out <- as.data.frame(pp_out) %>% mutate(dist = x^2 + y^2)


## directional: bottom > top
pp_btm1 <- rpoint(n, function(x,y) {100 * exp(-1*y)}, win = circle)
df_btm1 <- as.data.frame(pp_btm1) %>% mutate(dist = x^2 + y^2)

pp_btm2 <- rpoint(n, function(x,y) {100 * exp(-2*y)}, win = circle)
df_btm2 <- as.data.frame(pp_btm2) %>% mutate(dist = x^2 + y^2)

pp_btm3 <- rpoint(n, function(x,y) {100 * exp(-3*y)}, win = circle)
df_btm3 <- as.data.frame(pp_btm3) %>% mutate(dist = x^2 + y^2)

pp_btm4 <- rpoint(n, function(x,y) {100 * exp(-4*y)}, win = circle)
df_btm4 <- as.data.frame(pp_btm4) %>% mutate(dist = x^2 + y^2)

pp_btm5 <- rpoint(n, function(x,y) {100 * exp(-5*y)}, win = circle)
df_btm5 <- as.data.frame(pp_btm5) %>% mutate(dist = x^2 + y^2)

pp_btm6 <- rpoint(n, function(x,y) {100 * exp(-6*y)}, win = circle)
df_btm6 <- as.data.frame(pp_btm6) %>% mutate(dist = x^2 + y^2)

pp_btm7 <- rpoint(n, function(x,y) {100 * exp(-7*y)}, win = circle)
df_btm7 <- as.data.frame(pp_btm7) %>% mutate(dist = x^2 + y^2)

pp_btm8 <- rpoint(n, function(x,y) {100 * exp(-8*y)}, win = circle)
df_btm8 <- as.data.frame(pp_btm8) %>% mutate(dist = x^2 + y^2)

pp_btm9 <- rpoint(n, function(x,y) {100 * exp(-9*y)}, win = circle)
df_btm9 <- as.data.frame(pp_btm9) %>% mutate(dist = x^2 + y^2)

pp_btm10 <- rpoint(n, function(x,y) {100 * exp(-10*y)}, win = circle)
df_btm10 <- as.data.frame(pp_btm10) %>% mutate(dist = x^2 + y^2)
```


## Plots Point Patterns

```{r function-plot-distributions}
plot_dist <- function(data, title, color = TRUE) {

  base <- 
    ggplot(as.data.frame(circle), aes(x, y)) + 
    geom_path(color = "black", alpha = .33, size = 2) + 
    coord_fixed() + 
    scale_x_continuous(limits = c(-1, 1)) +
    scale_y_continuous(limits = c(-1, 1))
  
  if (isTRUE(color)) {
     base + 
      geom_point(data = data, aes(color = dist), alpha = .7) +
      scale_color_gradient(low = "#003F4C", high = "#B200B2", guide = "none") + 
      ggtitle(title)
  } else {
    base + 
      geom_point(data = data, alpha = .7) + 
      ggtitle(title)
  }
}
```

### Distribution Scenarios

```{r plots-distributions, fig.width=15, fig.height=10}
## no color versions ###########################################################

## random
gg_rand_nc <- plot_dist(df_rand, "**Random**", color = FALSE)

## uniform
#gg_unif_nc <- plot_dist(df_unif, "**Uniform** (?)", color = FALSE)
gg_sunf_nc <- plot_dist(df_sunf, "**Uniform** (sunflower)", color = FALSE)  

## directional: inner > outer
gg_inn_nc <- plot_dist(df_inn, "**Inner to Outer**", color = FALSE)

## directional: outer > inner
gg_out_nc <- plot_dist(df_out, "**Outer to Inner**", color = FALSE)               

## directional: bottom > top
gg_btm1_nc  <- plot_dist(df_btm1,  "**Bottom to Top** (exp(-y))", color = FALSE)
gg_btm2_nc  <- plot_dist(df_btm2,  "**Bottom to Top** (exp(-2*y))", color = FALSE)
gg_btm3_nc  <- plot_dist(df_btm3,  "**Bottom to Top** (exp(-3*y))", color = FALSE)
gg_btm4_nc  <- plot_dist(df_btm4,  "**Bottom to Top** (exp(-4*y))", color = FALSE)
gg_btm5_nc  <- plot_dist(df_btm5,  "**Bottom to Top** (exp(-5*y))", color = FALSE)
gg_btm6_nc  <- plot_dist(df_btm6,  "**Bottom to Top** (exp(-6*y))", color = FALSE)
gg_btm7_nc  <- plot_dist(df_btm7,  "**Bottom to Top** (exp(-7*y))", color = FALSE)
gg_btm8_nc  <- plot_dist(df_btm8,  "**Bottom to Top** (exp(-8*y))", color = FALSE)
gg_btm9_nc  <- plot_dist(df_btm9,  "**Bottom to Top** (exp(-9*y))", color = FALSE)
gg_btm10_nc <- plot_dist(df_btm10, "**Bottom to Top** (exp(-10*y))", color = FALSE)


## panel
(gg_sunf_nc | gg_btm2_nc | gg_inn_nc) / (gg_rand_nc | gg_btm5_nc | gg_out_nc)

ggsave(here::here("plots", "circular_distributions_nc.png"), width = 15, height = 10, dpi = 700)
```


#### Distribution Scenarios Colored by Distance

```{r plots-distributions-color, fig.width=15, fig.height=10}
## colored versions ############################################################

## random
gg_rand <- plot_dist(df_rand, "**Random**")

## uniform
#gg_unif <- plot_dist(df_unif, "**Uniform** (?)")
gg_sunf <- plot_dist(df_sunf, "**Uniform** (sunflower)")  

## directional: inner > outer
gg_inn <- plot_dist(df_inn, "**Inner to Outer**")

## directional: outer > inner
gg_out <- plot_dist(df_out, "**Outer to Inner**")

## directional: bottom > top
gg_btm1  <- plot_dist(df_btm1,  "**Bottom to Top** (exp(-y))")
gg_btm2  <- plot_dist(df_btm2,  "**Bottom to Top** (exp(-2*y))")
gg_btm3  <- plot_dist(df_btm3,  "**Bottom to Top** (exp(-3*y))")
gg_btm4  <- plot_dist(df_btm4,  "**Bottom to Top** (exp(-4*y))")
gg_btm5  <- plot_dist(df_btm5,  "**Bottom to Top** (exp(-5*y))")
gg_btm6  <- plot_dist(df_btm6,  "**Bottom to Top** (exp(-6*y))")
gg_btm7  <- plot_dist(df_btm7,  "**Bottom to Top** (exp(-7*y))")
gg_btm8  <- plot_dist(df_btm8,  "**Bottom to Top** (exp(-8*y))")
gg_btm9  <- plot_dist(df_btm9,  "**Bottom to Top** (exp(-9*y))")
gg_btm10 <- plot_dist(df_btm10, "**Bottom to Top** (exp(-10*y))")


## panel
(gg_sunf | gg_btm2 | gg_inn) / (gg_rand | gg_btm5 | gg_out)

ggsave("plots/circular_distributions.png", width = 15, height = 10, dpi = 700)
```



### Variations of Bottom to Top Distributions

```{r plots-distributions-bottom-top, fig.width=24, fig.height=10}
## panel bottom > top
(gg_btm1_nc | gg_btm2_nc | gg_btm3_nc | gg_btm4_nc | gg_btm5_nc) / (gg_btm6_nc | gg_btm7_nc | gg_btm8_nc | gg_btm9_nc | gg_btm10_nc)

ggsave("plots/circular_distributions_btms_nc.png", width = 24, height = 10, dpi = 700)
```


#### Distribution Scenarios Colored by Distance

```{r plots-distributions-color-bottom-top, fig.width=24, fig.height=10}
## panel bottom > top
(gg_btm1 | gg_btm2 | gg_btm3 | gg_btm4 | gg_btm5) / (gg_btm6 | gg_btm7 | gg_btm8 | gg_btm9 | gg_btm10)

ggsave("plots/circular_distributions_btms.png", width = 24, height = 10, dpi = 700)
```


## Plots Proportion Monitored

```{r function-plot-monitored-area}
plot_monitoring <- function(gg, data, circle_monitored) {
  gg + 
    geom_path(data = as.data.frame(circle_monitored), color = "orange2", alpha = .2, size = 1.5) +
    geom_point(data = filter(data, dist < radius_monitored^2), color = "orange2")
}
```

```{r function-visualize-monitoring-all-distributions}
plot_monitoring_all <- function(proportion_covered, df_rand, df_sunf, df_inn, df_out, df_btm_2, df_btm_5) {
  
  ## radius acoustic monitoring via % area covered + length rotor blades
  area_rotor <- pi * radius_rotor^2
  area_monitored <- area_rotor * proportion_covered * 2   
  ## times 2 because we only use the lower half of the circle = half of the area later
  radius_monitored <- sqrt(area_monitored / pi)
  
  circle_monitored <- disc(
    radius = radius_monitored,
    centre = c(0, 0), 
    mask = FALSE, 
    npoly = 5000
  )
  
  circle_half_monited <-
    as.data.frame(circle_monitored) %>% 
    filter(y <= 0)
    
  ## random
  gg_rand_r <- gg_rand_nc + 
    geom_path(data = circle_half_monited, color = "orange2", alpha = .2, size = 1.5) +
    geom_point(data = filter(df_rand, dist < radius_monitored^2 & y <= 0), color = "orange2")
  
  ## uniform
  # gg_unif_r <- gg_unif_nc + 
  #   geom_path(data = circle_half_monited, color = "orange2", alpha = .2, size = 1.5) +
  #   geom_point(data = filter(df_unif, dist < radius_monitored^2 & y <= 0), color = "orange2")
  
  gg_sunf_r <- gg_sunf_nc + 
    geom_path(data = circle_half_monited, color = "orange2", alpha = .2, size = 1.5) +
    geom_point(data = filter(df_sunf, dist < radius_monitored^2 & y <= 0), color = "orange2")

  ## directional: inner > outer
  gg_inn_r <- gg_inn_nc + 
    geom_path(data = circle_half_monited, color = "orange2", alpha = .2, size = 1.5) +
    geom_point(data = filter(df_inn, dist < radius_monitored^2 & y <= 0), color = "orange2")
  
  ## directional: outer > inner
  gg_out_r <- gg_out_nc + 
    geom_path(data = circle_half_monited, color = "orange2", alpha = .2, size = 1.5) +
    geom_point(data = filter(df_out, dist < radius_monitored^2 & y <= 0), color = "orange2")
  
  
  ## bottom > top
  gg_btm2_r <- gg_btm2_nc + 
    geom_path(data = circle_half_monited, color = "orange2", alpha = .2, size = 1.5) +
    geom_point(data = filter(df_btm2, dist < radius_monitored^2 & y <= 0), color = "orange2")
  
  gg_btm5_r <- gg_btm5_nc + 
    geom_path(data = circle_half_monited, color = "orange2", alpha = .2, size = 1.5) +
    geom_point(data = filter(df_btm5, dist < radius_monitored^2 & y <= 0), color = "orange2")
  
  
  ## panel
  p <- (gg_sunf_r | gg_btm2_r | gg_inn_r) / (gg_rand_r | gg_btm5_r | gg_out_r)
}
```


### Monitoring Covers 50%

```{r panel-monitored-50, fig.width=15, fig.height=15}
(panel_monitored <- plot_monitoring_all(
  proportion_covered = .5, df_rand, df_sunf, df_inn, df_out, df_btm_2, df_btm_5
))
ggsave("plots/circular_distributions_area_monitored_50.png", width = 15, height = 10, dpi = 700)
```


### Monitoring Covers 40%

```{r panel-monitored-40, fig.width=15, fig.height=15}
(panel_monitored <- plot_monitoring_all(
  proportion_covered = .4, df_rand, df_sunf, df_inn, df_out, df_btm_2, df_btm_5
))
ggsave("plots/circular_distributions_area_monitored_40.png", width = 15, height = 10, dpi = 700)
```


### Monitoring Covers 30%

```{r panel-monitored-30, fig.width=15, fig.height=15}
(panel_monitored <- plot_monitoring_all(
  proportion_covered = .3, df_rand, df_sunf, df_inn, df_out, df_btm_2, df_btm_5
))
ggsave("plots/circular_distributions_area_monitored_30.png", width = 15, height = 10, dpi = 700)
```


### Monitoring Covers 20%

```{r panel-monitored-20, fig.width=15, fig.height=15}
(panel_monitored <- plot_monitoring_all(
  proportion_covered = .2, df_rand, df_sunf, df_inn, df_out, df_btm_2, df_btm_5
))
ggsave("plots/circular_distributions_area_monitored_20.png", width = 15, height = 10, dpi = 700)
```


### Monitoring Covers 10%

```{r panel-monitored-10, fig.width=15, fig.height=15}
(panel_monitored <- plot_monitoring_all(
  proportion_covered = .1, df_rand, df_sunf, df_inn, df_out, df_btm_2, df_btm_5
))
ggsave("plots/circular_distributions_area_monitored_10.png", width = 15, height = 10, dpi = 700)
```


### Monitoring Covers 5%

```{r panel-monitored-5, fig.width=15, fig.height=15}
(panel_monitored <- plot_monitoring_all(
  proportion_covered = .05, df_rand, df_sunf, df_inn, df_out, df_btm_2, df_btm_5
))
ggsave("plots/circular_distributions_area_monitored_05.png", width = 15, height = 10, dpi = 700)
```

***

<details><summary>Session Info</summary>

```{r sessionInfo}
Sys.time()
sessionInfo()
```

</details>
