---
title: "Turbine Collision Risk: Overview Plots Distributions"
description: ""
author:
    - name: "Cédric Scherer"
      url: https://cedricscherer.com
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://www.izw-berlin.de/en/home.html
      orcid_id: 0000-0003-0645-5666
    - name: "Christian Voigt"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://www.izw-berlin.de/en/home.html
      orcid_id: 0000-0002-0706-3974
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate
        code_folding: true  
        toc: true            
        toc_depth: 2         
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 15, fig.height = 10,
                      dev = "ragg_png", res = 1000, retina = 1)
```

## Preparation

```{r prep}
library(tidyverse)
library(here)
library(ggtext)
library(spatstat.core)
library(colorspace)
library(here)
library(patchwork)

theme_set(theme_void(base_size = 20, base_family = "Open Sans"))
theme_update(
  plot.title = element_markdown(hjust = .5, face = "bold", size = 30),
  plot.title.position = "plot",
  plot.margin = margin(rep(10, 4)),
  plot.background = element_rect(fill = "white", color = "white")
)

## source funcrions to generate distributions of bat passes
source(here("R", "src", "generate-distributions.R"))
```

## Research Question

* Predictive power of the acoustic monitoring

> Is the predictive power of the current acoustic monitoring sufficient enough to estimate the true number of killed bats?

### Predictions

The predictive power of the acoustic monitoring for the extrapolation of the expected number of stroke victims is decreasing

* in case the crossing bats are not distributed uniformly or randomly.

* with increasing length of the rotor blades.

* for species with high-frequency echo calls.


### Open Questions

* wie die Dichte skalieren zwischen großen und kleinen Windrädern?
  - z.B. von innen nach außen abhängig von relativer oder absoluter Distanz zum Mittelpunkt?

* globale oder lokale Anzahl an Fledermäusen konstant halten?

## Inputs

We have the following parameters we can vary:

* length of rotor blades (`radius_rotor`) - 60 m versus 33 m
+ determines area of wind turbine (`area_rotor` as `pi * radius_rotor^2`)
* proportion of area covered by acoustic monitoring (`proportion_covered`)
+ determines area of acoustic monitoring (`area_monitored` as `area_rotor * proportion_covered`)
+ determines radius to detect bars (`radius_monitored` as `sqrt(area_monitored / pi)`)
* number of bats simulated (`n`)
+ could be either total (for now) or number monitored (maybe later)



```{r function-plot-distributions}
plot_dist <- function(data, title = NULL, color = NULL, shape = NULL, size = 1) {

  df_rotor <- as.data.frame(
    disc(radius = 1, centre = c(0, 0),  mask = FALSE, npoly = 5000)
  )
  
  area_monitored <- pi * unique(data$prop_monitored) * 2   ## pi *1^2 -> area 
  ## times 2 because we only use the lower half of the circle = half of the area later
  radius_monitored <- sqrt(area_monitored / pi)
  
  df_monitored <- 
    as.data.frame(
      disc(radius = radius_monitored, centre = c(0, 0), mask = FALSE,  npoly = 5000)
    ) %>% 
    filter(y <= 0)
  
  base <- 
    ggplot(df_rotor, aes(x, y)) + 
    geom_path(color = "black", alpha = .33, size = 2.5) + 
    coord_fixed() + 
    scale_x_continuous(limits = c(-1, 1)) +
    scale_y_continuous(limits = c(-1, 1))
  
  if (!is.null(color) & !is.null(shape)) {
    
     base + 
       geom_path(data = df_monitored, color = desaturate(lighten(color, .25), .25), size = 1.5) +
       geom_point(data = data, aes(color = monitored, shape = fatality, size = fatality, alpha = fatality, stroke = 1.2)) +
       scale_color_manual(values = c("grey20", color), guide = "none") + 
       scale_shape_manual(values = c(1, shape), guide = "none") +  
       scale_size_manual(values = c(2, 10), guide = "none") +  
       scale_alpha_manual(values = c(.2, 1), guide = "none") + 
       ggtitle(title)
    
  } else if (!is.null(color) & is.null(shape)){ 
    
    base + 
       geom_path(data = df_monitored, color = desaturate(lighten(color, .25), .25), size = 1.5) +
       geom_point(data = data, aes(color = monitored), alpha = .2, size = size) +
       scale_color_manual(values = c("grey20", color), guide = "none") + 
       ggtitle(title)
    
  } else {
    
    base + 
      geom_point(data = data, alpha = .2, size = size) + 
      ggtitle(title)
    
  }
}
```


## Comparison Distribution Scenarios

```{r example-distributions}
m <- .2     ## proportion monitored
n <- 1200L  ## number of basses
s <- 1L     ## seed

## uniform
df_uni  <- generate_distribution(distribution = "uniform", prop_monitored = m, n = n, seed = s, var = FALSE)

## random
df_ran  <- generate_distribution(distribution = "random",  prop_monitored = m, n = n, seed = s, var = FALSE)

## inner > outer (basic)
df_inn1  <- generate_distribution(distribution = "inner",   prop_monitored = m, n = n, seed = s, var = FALSE, skewness = 1)

## inner > outer (basic)
df_inn3  <- generate_distribution(distribution = "inner",   prop_monitored = m, n = n, seed = s, var = FALSE, skewness = 3)

## outer > inner (basic)
df_out1  <- generate_distribution(distribution = "outer",   prop_monitored = m, n = n, seed = s, var = FALSE, skewness = 1)

## outer > inner (basic)
df_out3  <- generate_distribution(distribution = "outer",   prop_monitored = m, n = n, seed = s, var = FALSE, skewness = 3)

## bottom > top (basic)
df_bot1 <- generate_distribution(distribution = "bottom",  prop_monitored = m, n = n, seed = s, var = FALSE, skewness = 1)

## bottom > top (extreme)
df_bot3 <- generate_distribution(distribution = "bottom",  prop_monitored = m, n = n, seed = s, var = FALSE, skewness = 3)

## top > bottom (basic)
df_top1 <- generate_distribution(distribution = "top",     prop_monitored = m, n = n, seed = s, var = FALSE, skewness = 1)

## top > bottom (extreme)
df_top3 <- generate_distribution(distribution = "top",     prop_monitored = m, n = n, seed = s, var = FALSE, skewness = 3)
```


```{r plots-distributions-rotor, fig.width=24, fig.height=12.5}
gg_uni_r  <- plot_dist(df_uni,  title = "a) uniform")
gg_ran_r  <- plot_dist(df_ran,  title = "b) random")
gg_inn1_r <- plot_dist(df_inn1, title = "c) inner — weak")
gg_inn3_r <- plot_dist(df_inn3, title = "d) inner — strong")
gg_out1_r <- plot_dist(df_out1, title = "e) outer — weak")
gg_out3_r <- plot_dist(df_out3, title = "f) outer — strong")
gg_bot1_r <- plot_dist(df_bot1, title = "g) bottom — weak")
gg_bot3_r <- plot_dist(df_bot3, title = "h) bottom — strong")
gg_top1_r <- plot_dist(df_top1, title = "i) top — weak")
gg_top3_r <- plot_dist(df_top3, title = "j) top — strong")

## panel
p_r <- (gg_uni_r | gg_inn1_r | gg_out1_r | gg_bot1_r | gg_top1_r) / (gg_ran_r | gg_inn3_r | gg_out3_r | gg_bot3_r | gg_top3_r)

p_r

ggsave(here("plots", "fig1_distributions_all_rotor.png"), width = 24, height = 12.5, dpi = 800)

## portrait-format
# p_r_l <- 
#   wrap_plots(gg_uni_r, gg_ran_r, gg_inn1_r, gg_inn3_r, gg_out1_r, 
#              gg_out3_r, gg_bot1_r, gg_bot3_r, gg_top1_r, gg_top3_r, ncol = 2) * 
#   theme(plot.margin = margin(5, 40, 5, 40))
# 
# ggsave(here("plots", "distributions", "distributions_all_rotor_long.png"), width = 12, height = 24, dpi = 800)
```


```{r plots-distributions-monitoring, fig.width=24, fig.height=12.5}
gg_uni_m  <- plot_dist(df_uni,  color = "orange2", title = "a) uniform")
gg_ran_m  <- plot_dist(df_ran,  color = "orange2", title = "b) random")
gg_inn1_m <- plot_dist(df_inn1, color = "orange2", title = "c) inner — weak")
gg_inn3_m <- plot_dist(df_inn3, color = "orange2", title = "d) inner — strong")
gg_out1_m <- plot_dist(df_out1, color = "orange2", title = "e) outer — weak")
gg_out3_m <- plot_dist(df_out3, color = "orange2", title = "f) outer — strong")
gg_bot1_m <- plot_dist(df_bot1, color = "orange2", title = "g) bottom — weak")
gg_bot3_m <- plot_dist(df_bot3, color = "orange2", title = "h) bottom — strong")
gg_top1_m <- plot_dist(df_top1, color = "orange2", title = "i) top — weak")
gg_top3_m <- plot_dist(df_top3, color = "orange2", title = "j) top — strong")

## panel
p_m <- (gg_uni_m | gg_inn1_m | gg_out1_m | gg_bot1_m | gg_top1_m) / (gg_ran_m | gg_inn3_m | gg_out3_m | gg_bot3_m | gg_top3_m) 

p_m

ggsave(here("plots", "distributions", "distributions_all_monitored.png"), width = 24, height = 12.5, dpi = 800)
```


```{r plots-distributions-fatalities, fig.width=24, fig.height=12.5}
gg_uni_f  <- plot_dist(df_uni,  color = "orange2", shape = 4, title = "a) uniform")
gg_ran_f  <- plot_dist(df_ran,  color = "orange2", shape = 4, title = "b) random")
gg_inn1_f <- plot_dist(df_inn1, color = "orange2", shape = 4, title = "c) inner — weak")
gg_inn3_f <- plot_dist(df_inn3, color = "orange2", shape = 4, title = "d) inner — strong")
gg_out1_f <- plot_dist(df_out1, color = "orange2", shape = 4, title = "e) outer — weak")
gg_out3_f <- plot_dist(df_out3, color = "orange2", shape = 4, title = "f) outer — strong")
gg_bot1_f <- plot_dist(df_bot1, color = "orange2", shape = 4, title = "g) bottom — weak")
gg_bot3_f <- plot_dist(df_bot3, color = "orange2", shape = 4, title = "h) bottom — strong")
gg_top1_f <- plot_dist(df_top1, color = "orange2", shape = 4, title = "i) top — weak")
gg_top3_f <- plot_dist(df_top3, color = "orange2", shape = 4, title = "j) top — strong")

## panel
p_f <- (gg_uni_f | gg_inn1_f | gg_out1_f | gg_bot1_f | gg_top1_f) / (gg_ran_f | gg_inn3_f | gg_out3_f | gg_bot3_f | gg_top3_f) 

p_f

ggsave(here("plots", "distributions", "distributions_all_fatalities.png"), width = 24, height = 12.5, dpi = 800)
```


## Plots Example Distributions


```{r plots-example-distributions-setup}
seed <- 123L
distribution <- "inner"
color <- "orange2"

theme_update(plot.title = element_markdown(size = 20))
```


### Small radius (30m) and low-frequency bats (20 kHz) 

```{r plots-example-distributions-small-low, fig.width=5, fig.height=5.2}
## small radius (30m) and low-frequency bats (20 kHz) 
##   -> small n             -> larger prop_monitored
small <- 100L
low_30 <- .5

df_30_low <- generate_distribution(n = small, prop_monitored = low_30, distribution = distribution, seed = seed, var = FALSE, skewness = 2)

(gg_d_30_low  <- plot_dist(df_30_low, size = 2, title = "30m radius + low-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_30m_low_freq_rotor.png")), width = 5, height = 5.2, dpi = 800)

(gg_m_30_low <- plot_dist(df_30_low, size = 2, color = color, title = "30m radius + low-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_30m_low_freq_monitored.png")), width = 5, height = 5.2, dpi = 800)

(gg_f_30_low <- plot_dist(df_30_low, color = color, shape = 4, title = "30m radius + low-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_30m_low_freq_fatalities.png")), width = 5, height = 5.2, dpi = 800)
```


### Small radius (30m) and high-frequency bats (40 kHz) 

```{r plots-example-distributions-small-high, fig.width=5, fig.height=5.2}
## small radius (30m) and high-frequency bats (40 kHz) 
##   -> small n             -> smaller prop_monitored
high_30 <- .17

df_30_high <- generate_distribution(n = small, prop_monitored = high_30, distribution = distribution, seed = seed, var = FALSE, skewness = 2)

(gg_d_30_high <- plot_dist(df_30_high, size = 2, title = "30m radius + high-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_30m_high_freq_rotor.png")), width = 5, height = 5.2, dpi = 800)

(gg_m_30_high <- plot_dist(df_30_high, size = 2, color = color, title = "30m radius + high-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_30m_high_freq_monitored.png")), width = 5, height = 5.2, dpi = 800)

(gg_f_30_high <- plot_dist(df_30_high, color = color, shape = 4, title = "30m radius + high-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_30m_high_freq_fatalities.png")), width = 5, height = 5.2, dpi = 800)
```


### Large radius (60m) and low-frequency bats (20 kHz)  

```{r plots-example-distributions-large-low, fig.width=5, fig.height=5.2}
## large radius (60m) and low-frequency bats (20 kHz)  
##   -> large n             -> larger prop_monitored
large <- 400L
low_60 <- .23

df_60_low <- generate_distribution(n = large, prop_monitored = low_60, distribution = distribution, seed = seed, var = FALSE, skewness = 2)

(gg_d_60_low <- plot_dist(df_60_low, size = 2, title = "60m radius + low-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_60m_low_freq_rotor.png")), width = 5, height = 5.2, dpi = 800)

(gg_m_60_low <- plot_dist(df_60_low, size = 2, color = color, title = "60m radius + low-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_60m_low_freq_monitored.png")), width = 5, height = 5.2, dpi = 800)

(gg_f_60_low <- plot_dist(df_60_low, color = color, shape = 4, title = "60m radius + low-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_60m_low_freq_fatalities.png")), width = 5, height = 5.2, dpi = 800)
```


### Large radius (60m) and high-frequency bats (40 kHz)  

```{r plots-example-distributions-large-high, fig.width=5, fig.height=5.2}
## large radius (60m) and high-frequency bats (40 kHz)  
##   -> large n             -> smaller prop_monitored
high_60 <- .04

df_60_high <- generate_distribution(n = large, prop_monitored = high_60, distribution = distribution, seed = seed, var = FALSE, skewness = 2)

(gg_d_60_high <- plot_dist(df_60_high, size = 2, title = "60m radius + high-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_60m_high_freq_rotor.png")), width = 5, height = 5.2, dpi = 800)

(gg_m_60_high <- plot_dist(df_60_high, size = 2, color = color, title = "60m radius + high-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_60m_high_freq_monitored.png")), width = 5, height = 5.2, dpi = 800)

(gg_f_60_high <- plot_dist(df_60_high, color = color, shape = 4, title = "60m radius + high-frequency"))
ggsave(here("plots", "distributions", paste0("distribution_example_", distribution, "_60m_high_freq_fatalities.png")), width = 5, height = 5.2, dpi = 800)
```


### Comparison Skewness

```{r}
plot_skewed <- function(dist, skewness) {
  g <- plot_distribution(
    generate_distribution(distribution = dist, skewness = skewness, 
                          n = 300L, prop_monitored = .01, seed = 123L),
    title = paste0("Skewness = ", skewness), color = "black", print = FALSE
  )
  
  g <- g + theme(plot.title = element_markdown(size = 15, face = "plain"))
  
  return(g)
}

skewness_levels <- c(1:5, 10, 15, 20)
n <- length(skewness_levels)

## inner > outer 
plots_inner <- purrr::map2(rep("inner",  n), skewness_levels, ~plot_skewed(dist = .x, skewness = .y))  ## c(1, 3, 5, 7, 9, 15, 30, 60)
wrap_plots(plots_inner, ncol = 4) + plot_annotation(title = "Inner > Outer")
ggsave(here::here("plots", "distributions", "distributions_gradient_inner.png"), width = 12, height = 7, dpi = 800)

## outer > inner
plots_outer <- purrr::map2(rep("outer",  n), skewness_levels, ~plot_skewed(dist = .x, skewness = .y))
wrap_plots(plots_outer, ncol = 4) + plot_annotation(title = "Outer > Inner")
ggsave(here::here("plots", "distributions", "distributions_gradient_outer.png"), width = 12, height = 7, dpi = 800)

## top > bottom
plots_top <- purrr::map2(rep("top",  n), skewness_levels, ~plot_skewed(dist = .x, skewness = .y))
wrap_plots(plots_top, ncol = 4) + plot_annotation(title = "Top > Bottom")
ggsave(here::here("plots", "distributions", "distributions_gradient_top.png"), width = 12, height = 7, dpi = 800)

## bottom > top
plots_bottom <- purrr::map2(rep("bottom", n), skewness_levels, ~plot_skewed(dist = .x, skewness = .y))
wrap_plots(plots_bottom, ncol = 4) + plot_annotation(title = "Bottom > Top")
ggsave(here::here("plots", "distributions", "distributions_gradient_bottom.png"), width = 12, height = 7, dpi = 800)
```


***

<details><summary>Session Info</summary>

```{r sessionInfo}
Sys.time()
sessionInfo()
```

</details>

