---
title: "Turbine Collision Risk: Generate Distribution Data"
description: ""
author:
    - name: "Cédric Scherer"
      url: https://cedricscherer.com
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://www.izw-berlin.de/en/home.html
      orcid_id: 0000-0003-0645-5666
    - name: "Christian Voigt"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://www.izw-berlin.de/en/home.html
      orcid_id: 0000-0002-0706-3974
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate
        code_folding: true  
        toc: true            
        toc_depth: 2         
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 18, fig.height = 10, 
                      dev = "ragg_png", res = 1000, retina = 1)
```

## Preparation 

```{r prep}
library(tidyverse)
library(here)
#library(ggtext)
#library(spatstat.core)
#library(patchwork)

theme_set(theme_light(base_size = 11.5, base_family = "Open Sans"))
theme_update(
  panel.grid.major = element_line(size = .3, color = "grey93"),
  panel.grid.minor = element_blank(),
  panel.grid.major.x = element_blank(),
  strip.background = element_rect(fill = "grey60", colour = "grey60"),
  strip.text = element_text(size = 14, face = "bold"),
  axis.title.x = element_text(size = 14, margin = margin(t = 12)),
  axis.title.y = element_text(size = 14, margin = margin(r = 12)),
  axis.text = element_text(size = 12),
  legend.title = element_text(size = 14, face = "bold"),
  legend.text = element_text(size = 12),
  plot.title = element_text(size = 24, face = "bold", margin = margin(5, 0, 5, 0)),
  plot.subtitle = element_text(margin = margin(5, 0, 25, 0), size = 17),
  plot.title.position = "plot",
  plot.margin = margin(rep(12, 4))
)

## source functions to generate and visualize distributions
source(here("R", "src", "generate-distributions.R"))
```

## Research Question

* Predictive power of the acoustic monitoring

> Is the predictive power of the current acoustic monitoring sufficient enough to estimate the true number of killed bats?

### Predictions

The predictive power of the acoustic monitoring for the extrapolation of the expected number of stroke victims is decreasing

* in case the crossing bats are not distributed uniformly or randomly.

* with increasing length of the rotor blades.

* for species with high-frequency echo calls.


### Open Questions

* wie die Dichte skalieren zwischen großen und kleinen Windrädern? 
  - z.B. von innen nach außen abhängig von relativer oder absoluter Distanz zum Mittelpunkt?
  
* globale oder lokale Anzahl an Fledermäusen konstant halten?

## Inputs

We have the following parameters we can vary:

* length of rotor blades (`radius_rotor`) - 60 m versus 33 m
  + determines area of wind turbine (`area_rotor` as `pi * radius_rotor^2`)
* proportion of area covered by acoustic monitoring (`proportion_covered`)
  + determines area of acoustic monitoring (`area_monitored` as `area_rotor * proportion_covered`)
  + determines radius to detect bars (`radius_monitored` as `sqrt(area_monitored / pi)`)
* number of bats simulated (`n`)
  + could be either total (for now) or number monitored (maybe later)


## Simulations 

### Generate Several Distributions

```{r run-simulations}
rds <- here("output", "data-proc", "simulation-runs.rds")
if (!file.exists(rds)) {
  scenarios <- simulate_multiple_distributions(
    runs = 200,   ## repetitions per combination, also used for seeding
    prop_monitored = c(.04, seq(.05, .5, by = .05), .23), 
    #n = c(100L, 250L, 500L, 1000L, 5000L, 15000L),
    n = c(100L, 200L, 400L, 800L, 1600L, 3200L),
    skewness = c(1, 3, 5)
  )
  write_rds(scenarios, rds)
} else {
  scenarios <- read_rds(rds)
}

scenarios_cleaned <-
  scenarios %>% 
  ## remove extremely skewed distributions
  filter(!str_detect(distribution, "_5$")) %>% 
  group_by(n, prop_monitored, distribution) %>% 
  mutate(diff = prop_monitored - median(prop_n_monitored)) %>% 
  ungroup() %>% 
  mutate(
    distribution = factor(
      distribution, 
      levels = c(
        "uniform", "random", 
        "inner_1", "inner_3",
        "outer_1", "outer_3", 
        "bottom_1", "bottom_3", 
        "top_1", "top_3"
      )
    ),
    prop_monitored_lab = paste0(prop_monitored * 100, "%"),
    prop_monitored_lab = fct_reorder(prop_monitored_lab, prop_monitored)
  )
```


## Visualizations Bat Passes

### Connected Error Bars 

Distribution (col) x Monitored Area (color) x Passes (x)

```{r lineplot-outcomes-summary, fig.width=13.5, fig.height=5.5}
scenarios_cleaned %>% 
  group_by(distribution, prop_monitored, n) %>% 
  summarize(mean = mean(prop_n_monitored), sd = sd(prop_n_monitored)) %>% 
  ungroup() %>% 
  mutate(
    base = mean - prop_monitored,
    min = base - sd, 
    max = base + sd
  ) %>% 
  ggplot(aes(n, base, color = prop_monitored, group = prop_monitored)) +
  geom_hline(aes(yintercept = 0), color = "grey75", size = 1.2)  + 
  geom_line(
    aes(color = prop_monitored, 
        color = after_scale(colorspace::desaturate(colorspace::lighten(color, .6), .4))),
    size = .7, show.legend = FALSE
  ) +
  geom_pointrange(aes(ymin = min, ymax = max), size = .4) +
  facet_wrap(~distribution, nrow = 2, dir = "v") +
  scale_x_continuous(expand = c(.04, .04), breaks = unique(scenarios_cleaned$n),
                     guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(expand = c(.012, .012), breaks = -5:5 / 10) +
  scico::scale_color_scico(
    palette = "bamako", end = .8, direction = -1, name = "Proportion\ncovered\nby AUD:",
    breaks = seq(.05, .5, by = .05), labels = scales::percent_format(accuracy = 1)
  ) +
  guides(color = guide_legend(keywidth = unit(.6, "lines"), keyheight = unit(1.2, "lines"))) +
  labs(x = "Number of bat passes", y = "Deviation from expected proportion") +
  theme(panel.spacing.x = unit(.6, "lines"), 
        axis.text.x = element_text(size = 9),
        axis.text.y = element_text(size = 12),
        legend.text = element_text(hjust = 1))

ggsave(here("plots", "bat_passes", "passes_recorded_mean_sd_lines_cont.pdf"), width = 17, height = 8.5, device = cairo_pdf)


scenarios_cleaned %>% 
  group_by(distribution, prop_monitored, n) %>% 
  summarize(mean = mean(prop_n_monitored), sd = sd(prop_n_monitored)) %>% 
  ungroup() %>% 
  mutate(
    base = mean - prop_monitored,
    min = base - sd, 
    max = base + sd
  ) %>% 
  ggplot(aes(factor(n), base, color = prop_monitored, group = prop_monitored)) +
  geom_hline(aes(yintercept = 0), color = "grey75", size = 1.2)  + 
  geom_line(
    aes(color = prop_monitored, 
        color = after_scale(colorspace::desaturate(colorspace::lighten(color, .6), .4))),
    size = .7, show.legend = FALSE
  ) +
  geom_pointrange(aes(ymin = min, ymax = max), size = .5) +
  facet_wrap(~distribution, nrow = 2, dir = "v") +
  scale_x_discrete(expand = c(.05, .05)) +
  scale_y_continuous(expand = c(.012, .012), breaks = -5:5 / 10) +
  scico::scale_color_scico(
    palette = "bamako", end = .8, direction = -1, name = "Proportion\ncovered\nby AUD:",
    breaks = seq(.05, .5, by = .05), labels = scales::percent_format(accuracy = 1)
  ) +
  guides(color = guide_legend(keywidth = unit(.6, "lines"), keyheight = unit(1.2, "lines"))) +
  labs(x = "Number of bat passes", y = "Deviation from expected proportion") +
  theme(panel.spacing.x = unit(.8, "lines"), axis.text = element_text(size = 10),
        legend.text = element_text(hjust = 1))

ggsave(here("plots", "bat_passes", "passes_recorded_mean_sd_lines_disc.pdf"), width = 13.5, height = 7.3, device = cairo_pdf)
```


### Heatmap

```{r heatmap-outcomes-summary, fig.width=14.5, fig.height=8.7}
scenarios_cleaned %>% 
  group_by(distribution, prop_monitored, prop_monitored_lab, n) %>% 
  summarize(mean = mean(prop_n_monitored), sd = sd(prop_n_monitored)) %>% 
  ungroup() %>% 
  mutate(
    base = mean - prop_monitored,
    scenario_highlight = ifelse(
      (n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5), "1", "0"
    ),
    label_highlight = ifelse(
      (n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5), 
      sprintf("%1.3f", base), NA_character_
    )
  ) %>% 
  ggplot(aes(factor(n), fct_rev(prop_monitored_lab))) +
  geom_tile(aes(fill = base), color = "white", size = .7) +
  geom_tile(aes(color = scenario_highlight), fill = "transparent", size = .8) +
  geom_text(
    aes(label = label_highlight), 
    color = "white", family = "Open Sans", size = 3.3, fontface = "bold"
  ) +
  geom_text(
    aes(label = label_highlight, alpha = abs(base) < .2), 
    color = "#212121", family = "Open Sans", size = 3.3, fontface = "bold"
  ) +
  facet_wrap(~distribution, nrow = 2, dir = "v") +
  coord_cartesian(expand = FALSE, clip = "off") +
  scale_color_manual(values = c("transparent", "#212121"), guide = "none") +
  scico::scale_fill_scico(
    palette = "roma", direction = 1, name = "Deviation from expected proportion",
    breaks = seq(-.5, .5, by = .1), midpoint = 0
  ) +
  scale_alpha_manual(values = c(0, 1), guide = "none") +
  guides(fill = guide_colorsteps(title.position = "top")) +
  labs(x = "Number of bat passes", y = "Proportion covered by AUD") +
  theme(panel.spacing = unit(.9, "lines"), 
        panel.background = element_rect(size = .7, color = "white", fill = "transparent"),
        panel.border = element_rect(color = "transparent", fill = "transparent"),
        axis.text = element_text(size = 11.5),
        axis.ticks = element_line(color = "transparent"),
        axis.ticks.length = unit(.3, "lines"),
        strip.text = element_text(color = "black"),
        strip.background = element_rect(color = "transparent", fill = "transparent"),
        legend.position = "top",
        legend.justification = "left",
        legend.key.width = unit(6, "lines"), legend.key.height = unit(.6, "lines"))

ggsave(here("plots", "bat_passes", "passes_recorded_mean_heatmap_horizontal.pdf"), width = 14.5, height = 8.7, device = cairo_pdf)
```

```{r heatmap-outcomes-summary-vertical, fig.width=13.5, fig.height=5.5}
scenarios_cleaned %>% 
  group_by(distribution, prop_monitored, prop_monitored_lab, n) %>% 
  summarize(mean = mean(prop_n_monitored), sd = sd(prop_n_monitored)) %>% 
  ungroup() %>% 
  mutate(
    base = mean - prop_monitored,
    scenario_highlight = ifelse(
      (n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5), "1", "0"
    ),
    label_highlight = ifelse(
      (n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5), 
      sprintf("%1.3f", base), NA_character_
    )
  ) %>% 
  ggplot(aes(prop_monitored_lab, fct_rev(factor(n)))) +
  geom_tile(aes(fill = base), color = "white", size = .7) +
  geom_tile(aes(color = scenario_highlight), fill = "transparent", size = .8) +
  geom_text(
    aes(label = label_highlight), 
    color = "white", family = "Open Sans", size = 3.3, fontface = "bold"
  ) +
  geom_text(
    aes(label = label_highlight, alpha = abs(base) < .2), 
    color = "#212121", family = "Open Sans", size = 3.3, fontface = "bold"
  ) +
  facet_wrap(~distribution, ncol = 2, dir = "h") +
  coord_cartesian(expand = FALSE, clip = "off") +
  scale_color_manual(values = c("transparent", "#212121"), guide = "none") +
  scico::scale_fill_scico(
    palette = "roma", direction = 1, name = "Deviation from expected proportion",
    breaks = seq(-.5, .5, by = .1), midpoint = 0
  ) +
  scale_alpha_manual(values = c(0, 1), guide = "none") +
  guides(fill = guide_colorsteps(title.position = "top")) +
  labs(x = "Proportion covered by AUD", y = "Number of bat passes") +
  theme(panel.spacing = unit(.9, "lines"), 
        panel.background = element_rect(size = .7, color = "white", fill = "transparent"),
        panel.border = element_rect(color = "transparent", fill = "transparent"),
        axis.text = element_text(size = 11.5),
        axis.ticks = element_line(color = "transparent"),
        axis.ticks.length = unit(.3, "lines"),
        strip.text = element_text(color = "black"),
        strip.background = element_rect(color = "transparent", fill = "transparent"),
        legend.position = "top",
        legend.justification = "left",
        legend.key.width = unit(6, "lines"), legend.key.height = unit(.6, "lines"))

ggsave(here("plots", "bat_passes", "passes_recorded_mean_heatmap_vertical.pdf"), width = 12, height = 13.2, device = cairo_pdf)
```


### Boxplots

##### Proportion of Passes Monitored (y) per Distribution (col) x Monitored Area (rows) x Passes (x)

```{r boxplots-passes-monitored-grid, fig.width=23, fig.height=13}
box <- 
  ggplot(scenarios_cleaned, aes(factor(n), prop_n_monitored)) +
  geom_hline(aes(yintercept = prop_monitored), color = "grey75", size = .7)  + 
  geom_boxplot(aes(color = diff), size = .4, outlier.shape = 1, outlier.size = .3) + 
  scale_y_continuous(labels = scales::percent_format(), 
                     sec.axis = dup_axis(name = "Area covered by AUD", breaks = NULL, labels = NULL)) +
  scale_color_gradient2(low = "firebrick", mid = "grey40", high = "firebrick", 
                        limits = c(-.5, .5), guide = "none") +
  labs(x = "Number of bat passes", y = "Proportion of passes monitored") +
  theme(panel.spacing.y = unit(.65, "lines"), axis.text = element_text(size = 9),
        axis.title.x = element_text(size = 18, face = "bold"), 
        axis.title.y = element_text(size = 18, face = "bold"), 
        strip.text.x = element_text(size = 18),
        strip.text.y = element_text(size = 16),
        axis.title.y.right = element_text(size = 21, color = "grey60", face = "bold", margin = margin(l = 12)))

## fixed y scale
box + facet_grid(prop_monitored_lab ~ distribution)
ggsave(here("plots", "bat_passes", "passes_recorded_boxplots_fixed.pdf"), width = 23, height = 13, device = cairo_pdf)

## free y scale
box + facet_grid(prop_monitored_lab ~ distribution, scale = "free_y") 
ggsave(here("plots", "bat_passes", "passes_recorded_boxplots_free.pdf"), width = 23, height = 13, device = cairo_pdf)
```


##### Difference Predicted vs. Expected (y) per Distribution (col) x AUD (x)

*for scenarios with 400 bat passes, all AUDs*

```{r boxplot-passes-difference-grid, fig.width=12, fig.height=9}
#colors <- c("dodgerblue", "firebrick")
#colors <- c("#28A87D", "#a87d28")
colors <- scico::scico(n = 9, palette = "roma")[c(8,2)]

## absolute
data_abs <- 
  scenarios_cleaned %>%
  filter(n == 400) %>% 
  filter(!prop_monitored %in% c(.04, .23)) %>% ## remove dedicated scenarios 
  mutate(diff_passes = (n_monitored / prop_monitored) - n) %>% 
  bind_rows(
    tibble(
      distribution = factor("uniform", levels = levels(scenarios_cleaned$distribution)),
      label = c("Overestimation", "Underestimation"),
      #prop_monitored_lab = factor("5%", levels = levels(scenarios_cleaned$prop_monitored_lab)), ## with dedicated scenarios
      prop_monitored_lab = factor("10%", levels = levels(scenarios_cleaned$prop_monitored_lab)), 
      diff_passes = c(625, -250),
      color = colors
    )
  )

data_abs %>% 
  filter(is.na(label)) %>% 
  ggplot(aes(prop_monitored_lab, diff_passes)) +
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = 0, ymax = Inf, fill = colors[1], alpha = .12) + 
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, fill = colors[2], alpha = .12) + 
  geom_text(data = data_abs, aes(label = label, color = color), hjust = 0, fontface = "bold", size = 6) +
  geom_hline(yintercept = 0, size = .6, linetype = "31", color = "grey75") +
  geom_boxplot(color = "grey45", width = .85, size = .5, 
               outlier.size = .8, outlier.alpha = .4, outlier.shape = 1) +
  stat_summary(geom = "point", shape = 18, size = 3, color = "#212121") +
  facet_wrap(~distribution, nrow = 2, dir = "v") + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(expand = c(.03, .03), breaks = seq(-800, 1600, by = 400)) +
  scale_color_identity() +
  labs(x = "Area covered by AUD",
       y = "Absolute difference of predicted versus expected bat passes") +#,
       #title = "How much do the actual numbers differ from predicted bat passes?",
       #subtitle = "Absolute difference of actual bat passes and monitored bat passes") +
  theme(axis.text.x = element_text(size = 11))

ggsave(here("plots", "bat_passes", "passes_difference_boxplots_abs.pdf"), width = 15, height = 8.2, device = cairo_pdf)



## relative
data_rel <- 
  scenarios_cleaned %>%
  filter(n == 400) %>% 
  filter(!prop_monitored %in% c(.04, .23)) %>% ## remove dedicated scenarios 
  mutate(diff_passes = ((n_monitored / prop_monitored) - n) / n) %>% 
  bind_rows(
    tibble(
      distribution = factor("uniform", levels = levels(scenarios_cleaned$distribution)),
      label = c("Overestimation", "Underestimation"),
      #prop_monitored_lab = factor("5%", levels = levels(scenarios_cleaned$prop_monitored_lab)), ## with dedicated scenarios
      prop_monitored_lab = factor("10%", levels = levels(scenarios_cleaned$prop_monitored_lab)),
      diff_passes = c(1.25, -.67),
      color = colors
    )
  )

data_rel %>% 
  filter(is.na(label)) %>% 
  ggplot(aes(prop_monitored_lab, diff_passes)) +
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = 0, ymax = Inf, fill = colors[1], alpha = .12) + 
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, fill = colors[2], alpha = .12) + 
  geom_text(data = data_rel, aes(label = label, color = color), hjust = 0, fontface = "bold", size = 6) +
  geom_hline(yintercept = 0, size = .6, linetype = "31", color = "grey75") +
  geom_boxplot(color = "grey45", width = .85, size = .5, 
               outlier.size = .8, outlier.alpha = .4, outlier.shape = 1) +
  stat_summary(geom = "point", shape = 18, size = 3, color = "#212121") +
  facet_wrap(~distribution, nrow = 2, dir = "v") + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(expand = c(.03, .03), breaks = seq(-1, 3.5, by = .5)) +
  scale_color_identity() +
  labs(x = "Area covered by AUD",
       y = "Relative difference of predicted versus expected bat passes") +#,
       #title = "How much do the actual numbers differ from predicted bat passes?",
       #subtitle = "Relative difference of actual bat passes and monitored bat passes") +
  theme(axis.text.x = element_text(size = 11))

ggsave(here("plots", "bat_passes", "passes_difference_boxplots_rel.pdf"), width = 15, height = 8.2, device = cairo_pdf)
```

*for dedicated scenarios*

```{r boxplot-passes-difference-scenarios, fig.width=12, fig.height=9}
## absolute
data_abs_scen <- 
  scenarios_cleaned %>% 
  filter((n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5)) %>% 
  mutate(
    diff_passes = (n_monitored / prop_monitored) - n,
    scenario = paste0("n = ", n, "\narea = ", prop_monitored*100, "%")
  ) %>% 
  bind_rows(
    tibble(
      distribution = factor("uniform", levels = levels(scenarios_cleaned$distribution)),
      label = c("Overestimation", "Underestimation"),
      scenario = "n = 100\narea = 50%",
      diff_passes = c(625, -250),
      color = colors
    )
  )
  
data_abs_scen %>%
  filter(is.na(label)) %>% 
  ggplot(aes(scenario, diff_passes)) +
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = 0, ymax = Inf, fill = colors[1], alpha = .12) + 
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, fill = colors[2], alpha = .12) + 
  geom_text(data = data_abs_scen, aes(label = label, color = color), hjust = .15, fontface = "bold", size = 5) +
  geom_hline(yintercept = 0, size = .6, linetype = "31", color = "grey75") +
  geom_boxplot(color = "grey45", size = .6, width = .5, 
               position = position_nudge(x = .05), 
               outlier.size = .9, outlier.shape = 1) +
  geom_point(color = "grey90", shape = "-", size = 10.1, 
             position = position_nudge(x = -.31)) +
  geom_point(color = "grey45", shape = "-", size = 10.1, alpha = .05, 
             position = position_nudge(x = -.31)) +
  stat_summary(geom = "point", shape = 18, size = 4.5, color = "#212121", 
               position = position_nudge(x = .05)) +
  facet_wrap(~distribution, nrow = 2, dir = "v") + 
  scale_y_continuous(expand = c(.04, .04), breaks = seq(-800, 1600, by = 400)) +
  scale_color_identity() +
  labs(x = "Scenario (bat passes x area covered by AUD)",
       y = "Absolute difference of predicted versus expected bat passes")

ggsave(here("plots", "bat_passes", "passes_difference_boxplots_abs_scenarios.pdf"), width = 12, height = 7.7, device = cairo_pdf)


## relative
data_rel_scen <- 
  scenarios_cleaned %>%
  filter((n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5)) %>% 
  mutate(
    diff_passes = ((n_monitored / prop_monitored) - n) / n,
    scenario = paste0("n = ", n, "\narea = ", prop_monitored*100, "%")
  ) %>% 
  bind_rows(
    tibble(
      distribution = factor("uniform", levels = levels(scenarios_cleaned$distribution)),
      label = c("Overestimation", "Underestimation"),
      scenario = "n = 100\narea = 50%",
      diff_passes = c(1.25, -.75),
      color = colors
    )
  )

data_rel_scen %>% 
  filter(is.na(label)) %>% 
  ggplot(aes(scenario, diff_passes)) +
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = 0, ymax = Inf, fill = colors[1], alpha = .12) + 
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, fill = colors[2], alpha = .12) + 
  geom_text(data = data_rel_scen, aes(label = label, color = color), hjust = .15, fontface = "bold", size = 5) +
  geom_hline(yintercept = 0, size = .6, linetype = "31", color = "grey75") +
  geom_boxplot(color = "grey45", size = .6, width = .5, 
               position = position_nudge(x = .05), 
               outlier.size = .9, outlier.shape = 1) +
  geom_point(color = "grey90", shape = "-", size = 10, 
             position = position_nudge(x = -.31)) +
  geom_point(color = "grey45", shape = "-", size = 10, alpha = .05, 
             position = position_nudge(x = -.31)) +
  stat_summary(geom = "point", shape = 18, size = 4.5, color = "#212121", 
               position = position_nudge(x = .05)) +
  facet_wrap(~distribution, nrow = 2, dir = "v") + 
  scale_y_continuous(expand = c(.04, .04), breaks = seq(-1, 3.5, by = .5)) +
  scale_color_identity() +
  labs(x = "Area covered by AUD",
       y = "Relative difference of predicted versus expected bat passes")

ggsave(here("plots", "bat_passes", "passes_difference_boxplots_rel_scenarios.pdf"), width = 12, height = 7.7, device = cairo_pdf)


## ALTERNATIVE: JITTER
data_rel_scen %>% 
  filter(is.na(label)) %>% 
  ggplot(aes(scenario, diff_passes)) +
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = 0, ymax = Inf, fill = colors[1], alpha = .12) + 
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, fill = colors[2], alpha = .12) + 
  geom_text(data = data_rel_scen, aes(label = label, color = color), hjust = .15, fontface = "bold", size = 5) +
  geom_hline(yintercept = 0, size = .6, linetype = "31", color = "grey75") +
  geom_boxplot(color = "grey45", size = .6, width = .45, 
               position = position_nudge(x = .25), 
               outlier.size = .9, outlier.shape = 1) +
  gghalves::geom_half_point(side = "l", range_scale = .7, width = .6, shape = 16, 
                            transformation = position_jitter(height = 0, seed = 2022),
                            color = "grey45", size = 1.1, alpha = .15) +
  stat_summary(geom = "point", shape = 18, size = 4.5, color = "#212121", 
               position = position_nudge(x = .25)) +
  facet_wrap(~distribution, nrow = 2, dir = "v") + 
  scale_y_continuous(expand = c(.04, .04), breaks = seq(-1, 3.5, by = .5)) +
  scale_color_identity() +
  labs(x = "Area covered by AUD",
       y = "Relative difference of predicted versus expected bat passes")

ggsave(here("plots", "bat_passes", "passes_difference_boxplots_rel_scenarios_alt.pdf"), width = 12, height = 7.7, device = cairo_pdf)
```

```{r convert-pdf-passes, include = FALSE}
## convert PDFs to PNGs
path <- here("plots", "bat_passes")
pdfs <- list.files(path, pattern = ".*pdf")
for(pdf in pdfs) {
  pdftools::pdf_convert(
    pdf = glue::glue("{path}/{pdf}"), 
    filenames = glue::glue("{path}/png/{str_remove(pdf, '.pdf')}.png"),
    format = "png", dpi = 700
  )
}
```


## Visualizations Fatalities

### Fatalities vs bat passes — What really happens

```{r plots-fatalities-passes-reality, fig.width=13.5, fig.height=3.2}
## with variation
scenarios_cleaned %>% 
  filter(prop_monitored == .05) %>% 
  ggplot(aes(n, n_fatalities)) +
  #geom_abline(slope = .01, intercept = 0, size = .6, color = "grey75") +
  geom_jitter(alpha = .02, width = 20, height = 0) +
  geom_quantile(quantiles = c(.25, .75), color = "dodgerblue3", size = .6) +
  geom_quantile(quantiles = c(.5), color = "red", size = .9) +
  facet_grid(~ distribution) +
  scale_x_continuous(expand = c(.1, .1)) +
  labs(x = "Number of bat passes (reality)",
       y = "Number of fatalities") + #,
       #title = "What really happens",
       #subtitle = "Number of fatalities per number of bat passes (1% correlation + variation)") +
  theme(panel.grid.major.y = element_blank(), axis.text.x = element_text(size = 10))

ggsave(here("plots", "fatalities", "fatalities_correlation_reality_var.pdf"), width = 13.5, height = 3.2, device = cairo_pdf)


## without variation
scenarios_cleaned %>% 
  filter(prop_monitored == .05) %>% 
  mutate(n_fatalities = round(n / 100)) %>% 
  ggplot(aes(n, n_fatalities)) +
  #geom_abline(slope = .01, intercept = 0, size = .6, color = "grey75") +
  geom_point(alpha = .02) +
  geom_quantile(quantiles = c(0.25, 0.75), color = "dodgerblue3", size = .6) +
  geom_quantile(quantiles = c(0.5), color = "red", size = .9) +
  facet_grid(~ distribution) +
  scale_x_continuous(expand = c(.1, .1)) +
  labs(x = "Number of bat passes (reality)",
       y = "Number of fatalities") + #,
       #title = "What really happens",
       #subtitle = "Number of fatalities per number of bat passes (1% correlation without variation)") +
  theme(panel.grid.major.y = element_blank(), axis.text.x = element_text(size = 10))

ggsave(here("plots", "fatalities", "fatalities_correlation_reality_fix.pdf"), width = 13.5, height = 3.2, device = cairo_pdf)
```

#### Fatalities vs bat passes — What we observe

```{r plots-fatalities-passes-monitored, fig.width=16, fig.height=11.5}
## with variation
## fixed x-scale
scenarios_cleaned %>% 
  ggplot(aes(n_monitored, n_fatalities)) +
  #geom_abline(aes(slope = .01*prop_monitored, intercept = 0), linetype = "13", size = .6, color = "grey75") +
  geom_point(alpha = .02) +
  geom_quantile(quantiles = c(0.25, 0.75), color = "dodgerblue3", size = .6) +
  geom_quantile(quantiles = c(0.5), color = "red", size = .9) +
  facet_grid(prop_monitored_lab  ~ distribution) +
  scale_x_continuous(limits = c(0, 550), breaks = c(1, 1:5*100)) +
  scale_y_continuous(sec.axis = dup_axis(name = "Proportion covered by AUD", breaks = NULL, labels = NULL)) +
  labs(x = "Number of bat passes (monitored)",
       y = "Number of fatalities") + #,
       #title = "What is detected",
       #subtitle = "Number of fatalities per number of monitored bat passes (1% correlation + variation)") +
  theme(panel.grid.major.y = element_blank(), panel.spacing.y = unit(.65, "lines"), axis.text = element_text(size = 10),
        axis.title.y.right = element_text(size = 16, color = "grey60", face = "bold", margin = margin(l = 12)))

ggsave(here("plots", "fatalities", "fatalities_correlation_monitored_var.pdf"), width = 16, height = 11.5, device = cairo_pdf)

## with variation
## free-ranging x-axis
scenarios_cleaned %>% 
  ggplot(aes(n_monitored, n_fatalities)) +
  #geom_abline(slope = .01, intercept = 0, linetype = "13", size = .6, color = "grey75") +
  geom_point(alpha = .02) +
  geom_quantile(quantiles = c(0.25, 0.75), color = "dodgerblue3", size = .6) +
  geom_quantile(quantiles = c(0.5), color = "red", size = .9) +
  facet_grid(prop_monitored_lab  ~ distribution, scales = "free_x") +
  #scale_x_continuous(breaks = c(1, 1:5*100)) +
  scale_y_continuous(sec.axis = dup_axis(name = "Proportion covered by AUD", breaks = NULL, labels = NULL)) +
  labs(x = "Number of bat passes (monitored)",
       y = "Number of fatalities") +#,
       #title = "What is detected",
       #subtitle = "Number of fatalities per number of monitored bat passes (1% correlation + variation); note the different x axis ranges") +
  theme(panel.grid.major.y = element_blank(), panel.spacing = unit(.65, "lines"), axis.text = element_text(size = 10),
        axis.title.y.right = element_text(size = 16, color = "grey60", face = "bold", margin = margin(l = 12)))

ggsave(here("plots", "fatalities", "fatalities_correlation_monitored_var_free.pdf"), width = 16, height = 11.5, device = cairo_pdf)

## with variation
## free-ranging x-axis (flipped!)
scenarios_cleaned %>% 
  ggplot(aes(n_monitored, n_fatalities)) +
  #geom_abline(slope = .01, intercept = 0, linetype = "13", size = .6, color = "grey75") +
  geom_point(alpha = .02) +
  geom_quantile(quantiles = c(0.25, 0.75), color = "dodgerblue3", size = .6) +
  geom_quantile(quantiles = c(0.5), color = "red", size = .9) +
  facet_grid(distribution ~ prop_monitored_lab, scales = "free_x") +
  #scale_x_continuous(breaks = c(1, 1:5*100)) +
  scale_x_continuous(sec.axis = dup_axis(name = "Proportion covered by AUD", breaks = NULL, labels = NULL)) +
  labs(y = "Number of bat passes (monitored)",
       x = "Number of fatalities") +#,
       #title = "What is detected",
       #subtitle = "Number of fatalities per number of monitored bat passes (1% correlation + variation); note the different x axis ranges") +
  theme(panel.grid.major.x = element_blank(), panel.spacing = unit(.65, "lines"), axis.text = element_text(size = 10),
        axis.title.x.top = element_text(size = 16, color = "grey60", face = "bold", margin = margin(b = 12)))

ggsave(here("plots", "fatalities", "fatalities_correlation_monitored_var_free_flipped.pdf"), width = 16, height = 11, device = cairo_pdf)


## without variation
scenarios_cleaned %>% 
  mutate(n_fatalities = round(n / 100)) %>% 
  ggplot(aes(n_monitored, n_fatalities)) +
  #geom_abline(slope = .01, intercept = 0, linetype = "13", size = .6, color = "grey75") +
  geom_point(alpha = .02) +
  geom_quantile(quantiles = c(0.25, 0.75), color = "dodgerblue3", size = .6) +
  geom_quantile(quantiles = c(0.5), color = "red", size = .9) +
  facet_grid(prop_monitored_lab  ~ distribution) +
  scale_x_continuous(limits = c(0, 550), breaks = c(1, 1:5*100)) +
  scale_y_continuous(sec.axis = dup_axis(name = "Proportion covered by AUD", breaks = NULL, labels = NULL)) +
  labs(x = "Number of bat passes (monitored)",
       y = "Number of fatalities") +#,
       #title = "What is detected",
       #subtitle = "Number of fatalities per number of monitored bat passes (1% correlation without variation)") +
  theme(panel.grid.major.y = element_blank(), panel.spacing.y = unit(.65, "lines"), axis.text = element_text(size = 10),
        axis.title.y.right = element_text(size = 16, color = "grey60", face = "bold", margin = margin(l = 12)))

ggsave(here("plots", "fatalities", "fatalities_correlation_monitored_fix.pdf"), width = 16, height = 11.5, device = cairo_pdf)
```


#### Summaries (WIP)

```{r, eval=FALSE}
scenarios_fat_pred <-
  scenarios_cleaned %>% 
  mutate(
    n_fatalities_expected = n / 100,
    n_fatalities_predicted = n_monitored / 100 ,
    #n_fatalities_predicted = n_monitored * (prop_monitored*100) / 100 ,
    diff_fatalities = n_fatalities_expected - n_fatalities_predicted
  )

scenarios_fat_pred %>% 
  ggplot(aes(n_fatalities_expected, n_fatalities_predicted)) +
  geom_hline(yintercept = 0, size = .6, color = "grey75") +
  geom_abline(slope = 1, intercept = 0, linetype = "13", size = .6, color = "grey75") +
  geom_point(shape = 20, alpha = .0025, size = 2) +
  geom_quantile(quantiles = c(0.25, 0.75), color = "dodgerblue3", size = .6) +
  geom_quantile(quantiles = c(0.5), color = "red", size = .9) +
  facet_grid(prop_monitored  ~ distribution) +
  labs(x = "Number of fatalities (expected, as 1% of all passes)",
       y = "Number of fatalities (predicted, as 1% of passes detected by acoustic monitoring)",
       title = "How good is the predicted fatality risk?",
       subtitle = "Absolute difference between number of fatalities based on acoustic monitoring versus expected (1% correlation + variation)") +
  theme(panel.grid.major.y = element_blank())

ggsave("./plots/scenarios_correlation_fatalities_exp_pred.pdf", width = 16, height = 16, device = cairo_pdf)
  



scenarios_fat_pred %>% 
  mutate(prop_monitored = as.factor(str_sub(prop_monitored, 2, nchar(prop_monitored)))) %>% 
  ggplot(aes(prop_monitored, diff_fatalities)) +
  geom_boxplot(color = "grey60", size = .3, outlier.size = .4, outlier.alpha = .2, outlier.shape = 20) +
  stat_summary(geom = "point", shape = 18, size = 3) +
  facet_wrap(~distribution, nrow = 1) + 
  scale_y_continuous(expand = c(.015, .015)) +
  labs(x = "Proportion covered by AUD",
       y = "Absolute difference in fatalities\nexpected – predicted",
       title = "How good is the predicted fatality risk?",
       subtitle = "Absolute difference of actual bat fatalities and predicted fatalies based on monitoring") +
  theme(axis.text.x = element_text(size = 8))

ggsave("./plots/scenarios_correlation_fatalities_difference_box.pdf", width = 18, height = 6, device = cairo_pdf)


scenarios_fat_pred %>% 
  mutate(prop_monitored = as.factor(str_sub(prop_monitored, 2, nchar(prop_monitored)))) %>% 
  ggplot(aes(prop_monitored, diff_fatalities / n_fatalities_expected)) +
  geom_boxplot(color = "grey60", size = .3, outlier.size = .4, outlier.alpha = .2, outlier.shape = 20) +
  stat_summary(geom = "point", shape = 18, size = 3) +
  facet_wrap(~distribution, nrow = 1) + 
  scale_y_continuous(expand = c(.015, .015)) +
  labs(x = "Proportion covered by AUD",
       y = "Relative difference in fatalities\n(expected – predicted) / expected",
       title = "How good is the predicted fatality risk?",
       subtitle = "Relative difference of actual bat fatalities and predicted fatalies based on monitoring") +
  theme(axis.text.x = element_text(size = 8))

ggsave("./plots/scenarios_correlation_fatalities_difference_prop_box.pdf", width = 18, height = 6, device = cairo_pdf)


scenarios_fat_pred %>% 
  mutate(prop_monitored = as.factor(str_sub(prop_monitored, 2, nchar(prop_monitored)))) %>% 
  ggplot(aes(prop_monitored, diff_fatalities)) +
  geom_jitter(color = "grey90", height = 0, alpha = .1, width = .3, size = .4) +
  geom_smooth(aes(group = 1), color = "grey40") +
  stat_summary(geom = "point", shape = 18, size = 3) +
  facet_wrap(~distribution, nrow = 1) +
  scale_y_continuous(expand = c(.008, .008)) +
  labs(x = "Proportion covered by AUD",
       y = "Absolute difference in fatalities\nexpected – predicted",
       title = "How good is the predicted fatality risk?") +
  theme(axis.text.x = element_text(size = 8))

ggsave("./plots/scenarios_correlation_fatalities_difference_smooth_jitter.pdf", width = 18, height = 6, device = cairo_pdf)

scenarios_fat_pred %>% 
  mutate(prop_monitored = as.factor(str_sub(prop_monitored, 2, nchar(prop_monitored)))) %>% 
  ggplot(aes(prop_monitored, diff_fatalities)) +
  ggbeeswarm::geom_quasirandom(color = "grey90", alpha = .5, width = .3, size = .4) +
  geom_smooth(aes(group = 1), color = "grey40") +
  stat_summary(geom = "point", shape = 18, size = 3) +
  facet_wrap(~distribution, nrow = 1) +
  scale_y_continuous(expand = c(.005, .005)) +
  labs(x = "Proportion covered by AUD",
       y = "Absolute difference in fatalities\nexpected – predicted",
       title = "How good is the predicted fatality risk?") +
  theme(axis.text.x = element_text(size = 8))

ggsave("./plots/scenarios_correlation_fatalities_difference_smooth_bee.pdf", width = 18, height = 6, device = cairo_pdf)

scenarios_fat_pred %>% 
  mutate(prop_monitored = as.factor(str_sub(prop_monitored, 2, nchar(prop_monitored)))) %>% 
  ggplot(aes(prop_monitored, diff_fatalities / n_fatalities_expected)) +
  ggbeeswarm::geom_quasirandom(color = "grey90", alpha = .5, width = .3, size = .4) +
  geom_smooth(aes(group = 1), color = "grey40") +
  stat_summary(geom = "point", shape = 18, size = 3) +
  facet_wrap(~distribution, nrow = 1) +
  scale_y_continuous(expand = c(.005, .005)) +
  labs(x = "Proportion covered by AUD",
       y = "Relative difference in fatalities\n(expected – predicted) / expected",
       title = "How good is the predicted fatality risk?",
       subtitle = "Relative difference of actual bat fatalities and predicted fatalies based on monitoring") +
  theme(axis.text.x = element_text(size = 8))

ggsave("./plots/scenarios_correlation_fatalities_difference_prop_smooth_bee.pdf", width = 18, height = 6, device = cairo_pdf)
```



```{r convert-pdf-fatalities, include = FALSE}
## convert PDFs to PNGs
path <- here("plots", "fatalities")
pdfs <- list.files(path, pattern = ".*pdf")
for(pdf in pdfs) {
  pdftools::pdf_convert(
    pdf = glue::glue("{path}/{pdf}"), 
    filenames = glue::glue("{path}/png/{str_remove(pdf, '.pdf')}.png"),
    format = "png", dpi = 700
  )
}
```


***

<details><summary>Session Info</summary>

```{r sessionInfo}
Sys.time()
sessionInfo()
```

</details>
