---
title: "Turbine Collision Risk: Generate Distribution Data"
description: ""
author:
    - name: "Cédric Scherer"
      url: https://cedricscherer.com
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://www.izw-berlin.de/en/home.html
      orcid_id: 0000-0003-0645-5666
    - name: "Christian Voigt"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://www.izw-berlin.de/en/home.html
      orcid_id: 0000-0002-0706-3974
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate
        code_folding: true  
        toc: true            
        toc_depth: 2         
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 18, fig.height = 10, 
                      dev = "ragg_png", res = 1000, retina = 1)
```

## Preparation 

```{r prep}
library(tidyverse)
library(here)
library(broom)

## source functions to generate and visualize distributions
source(here("R", "src", "generate-distributions.R"))
```

## Research Question

* Predictive power of the acoustic monitoring

> Is the predictive power of the current acoustic monitoring sufficient enough to estimate the true number of killed bats?

### Predictions

The predictive power of the acoustic monitoring for the extrapolation of the expected number of stroke victims is decreasing

* in case the crossing bats are not distributed uniformly or randomly.

* with increasing length of the rotor blades.

* for species with high-frequency echo calls.


### Open Questions

* wie die Dichte skalieren zwischen großen und kleinen Windrädern? 
  - z.B. von innen nach außen abhängig von relativer oder absoluter Distanz zum Mittelpunkt?
  
* globale oder lokale Anzahl an Fledermäusen konstant halten?

## Inputs

We have the following parameters we can vary:

* length of rotor blades (`radius_rotor`) - 60 m versus 33 m
  + determines area of wind turbine (`area_rotor` as `pi * radius_rotor^2`)
* proportion of area covered by acoustic monitoring (`proportion_covered`)
  + determines area of acoustic monitoring (`area_monitored` as `area_rotor * proportion_covered`)
  + determines radius to detect bars (`radius_monitored` as `sqrt(area_monitored / pi)`)
* number of bats simulated (`n`)
  + could be either total (for now) or number monitored (maybe later)


## Simulations Distributions

```{r run-simulations}
rds <- here("output", "data-proc", "simulation-runs-norm.rds")
if (!file.exists(rds)) {
  scenarios <- simulate_multiple_distributions(
    runs = 200,   ## repetitions per combination, also used for seeding
    prop_monitored = c(.04, seq(.05, .5, by = .05), .23), 
    #n = c(100L, 250L, 500L, 1000L, 5000L, 15000L),
    n = c(100L, 200L, 400L, 800L, 1600L, 3200L),
    skewness = c(1, 3, 5)
  )
  write_rds(scenarios, rds)
} else {
  scenarios <- read_rds(rds)
}

scenarios <-
  scenarios %>% 
   mutate(distribution = factor(
     distribution, 
     levels = c("uniform", "random", 
                "inner_1", "inner_3",
                "outer_1", "outer_3", 
                "bottom_1", "bottom_3", 
                "top_1", "top_3")
    )
  )
```


## Analysis

### Fitting per Distribution x Prop Monitored

```{r fittings}
lm_scenarios <- 
  scenarios %>% 
  ## remove extremely skewed distributions
  filter(!str_detect(distribution, "_5$")) %>%
  ## add id
  #arrange(n, prop_monitored, distribution) %>% 
  #group_by(distribution, prop_monitored, n) %>% 
  #mutate(id = cur_group_id(), passes = n) %>% 
  #filter(id %in% 1:3) %>% 
  #nest(data = -c(id, distribution, prop_monitored, passes)) %>%
  nest(data = -c(distribution, prop_monitored)) %>% 
  mutate(
    fit = map(data, ~ lm(n_fatalities ~ n_monitored, data = .x)),
    tidied = map(fit, tidy),
    glance = map(fit, broom::glance),
    augment = map(fit, broom::augment),
    rsq = glance %>% map_dbl('r.squared'),
    slope = tidied %>% map_dbl(function(x) x$estimate[2])
  ) #%>%
  #unnest(tidied)

fits_scenarios <-
  lm_scenarios %>% 
  #dplyr::select(distribution, passes, prop_monitored, rsq, slope)
  dplyr::select(distribution, prop_monitored, rsq, slope) %>% 
  group_by(prop_monitored) %>% 
  mutate(
    slope_diff = slope - slope[which(distribution == "uniform")],
    rsq_diff = rsq - rsq[which(distribution == "uniform")]
  )
```

```{r plot-fittings}
## R-squared -------------------------------------------------------------------
ggplot(fits_scenarios, aes(factor(prop_monitored), fct_rev(distribution), fill = rsq)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%1.2f", rsq), color = rsq < .5)) +
  scico::scale_fill_scico(palette = "tokyo", direction = -1) +
  scale_color_manual(values = c("white", "black"), guide = "none")

## differences
ggplot(fits_scenarios, aes(factor(prop_monitored), fct_rev(distribution), fill = rsq_diff)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%1.2f", rsq), color = rsq < .5)) +
  scico::scale_fill_scico(palette = "tokyo", direction = -1) +
  scale_color_manual(values = c("white", "black"), guide = "none")


## Slope -----------------------------------------------------------------------
ggplot(fits_scenarios, aes(factor(prop_monitored), fct_rev(distribution), fill = slope)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%2.2f", slope), color = slope > 5)) +
  scico::scale_fill_scico(palette = "hawaii") +
  scale_color_manual(values = c("white", "black"), guide = "none")

## log-scale
ggplot(fits_scenarios, aes(factor(prop_monitored), fct_rev(distribution), fill = log(slope))) +
  geom_tile() +
  geom_text(aes(label = sprintf("%2.2f", slope), color = log(slope) > -1)) +
  scico::scale_fill_scico(palette = "hawaii") +
  scale_color_manual(values = c("white", "black"), guide = "none")

## differences
ggplot(fits_scenarios, aes(factor(prop_monitored), fct_rev(distribution), fill = slope_diff)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%2.2f", slope_diff), color = slope_diff > 5)) +
  scico::scale_fill_scico(palette = "hawaii") +
  scale_color_manual(values = c("white", "black"), guide = "none")
```





### Fitting per Distribution x Prop Monitored x Bat Passes

```{r fittings-2}
lm_scenarios_n <- 
  scenarios %>% 
  ## remove extremely skewed distributions
  filter(!str_detect(distribution, "_5$")) %>%
  nest(data = -c(distribution, prop_monitored, n)) %>% 
  mutate(
    fit = map(data, ~ lm(n_fatalities ~ n_monitored, data = .x)),
    tidied = map(fit, tidy),
    glance = map(fit, broom::glance),
    augment = map(fit, broom::augment),
    rsq = glance %>% map_dbl('r.squared'),
    slope = tidied %>% map_dbl(function(x) x$estimate[2])
  ) 

fits_scenarios_n <-
  lm_scenarios_n %>% 
  dplyr::select(distribution, prop_monitored, n, rsq, slope) %>% 
  group_by(prop_monitored, n) %>% 
  mutate(
    slope_diff = slope - slope[which(distribution == "uniform")],
    rsq_diff = rsq - rsq[which(distribution == "uniform")]
  )
```

```{r plot-fittings-2}
## R-squared -------------------------------------------------------------------
ggplot(fits_scenarios_n, aes(factor(prop_monitored), fct_rev(factor(n)), fill = rsq)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%1.3f", round(rsq, 3)), color = rsq < .02)) +
  facet_wrap(~distribution, ncol = 2) +
  scico::scale_fill_scico(palette = "tokyo", direction = -1) +
  scale_color_manual(values = c("white", "black"), guide = "none")


## Slope -----------------------------------------------------------------------
ggplot(fits_scenarios_n, aes(factor(prop_monitored), fct_rev(factor(n)), fill = slope)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%4.1f", slope), color = slope > -1)) +
  facet_wrap(~distribution, ncol = 2) +
  scico::scale_fill_scico(palette = "hawaii") +
  scale_color_manual(values = c("white", "black"), guide = "none")
```


***

<details><summary>Session Info</summary>

```{r sessionInfo}
Sys.time()
sessionInfo()
```

</details>
