---
title: "Turbine Collision Risk: Generate Distribution Data"
description: ""
author:
    - name: "Cédric Scherer"
      url: https://cedricscherer.com
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://www.izw-berlin.de/en/home.html
      orcid_id: 0000-0003-0645-5666
    - name: "Christian Voigt"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://www.izw-berlin.de/en/home.html
      orcid_id: 0000-0002-0706-3974
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate
        code_folding: true  
        toc: true            
        toc_depth: 2         
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 18, fig.height = 10, 
                      dev = "ragg_png", res = 1000, retina = 1)
```

## Preparation 

```{r prep}
library(tidyverse)
library(here)
library(broom)
library(patchwork)

theme_set(theme_light(base_size = 11.5, base_family = "Open Sans"))
theme_update(
  panel.grid.major = element_line(size = .3, color = "grey93"),
  panel.grid.minor = element_blank(),
  panel.grid.major.x = element_blank(),
  strip.background = element_rect(fill = "grey60", colour = "grey60"),
  strip.text.x = element_text(hjust = 0),
  strip.text = element_text(size = 14, face = "bold"),
  axis.title.x = element_text(size = 14, margin = margin(t = 12)),
  axis.title.y = element_text(size = 14, margin = margin(r = 12)),
  axis.text = element_text(size = 12),
  legend.title = element_text(size = 14, face = "bold"),
  legend.text = element_text(size = 12),
  plot.title = element_text(size = 24, face = "bold", margin = margin(5, 0, 5, 0)),
  plot.subtitle = element_text(margin = margin(5, 0, 25, 0), size = 17),
  plot.title.position = "plot",
  plot.margin = margin(rep(12, 4))
)

## source functions to generate and visualize distributions
source(here("R", "src", "generate-distributions.R"))
```

## Research Question

* Predictive power of the acoustic monitoring

> Is the predictive power of the current acoustic monitoring sufficient enough to estimate the true number of killed bats?

### Predictions

The predictive power of the acoustic monitoring for the extrapolation of the expected number of stroke victims is decreasing

* in case the crossing bats are not distributed uniformly or randomly.

* with increasing length of the rotor blades.

* for species with high-frequency echo calls.


### Open Questions

* wie die Dichte skalieren zwischen großen und kleinen Windrädern? 
  - z.B. von innen nach außen abhängig von relativer oder absoluter Distanz zum Mittelpunkt?
  
* globale oder lokale Anzahl an Fledermäusen konstant halten?

## Inputs

We have the following parameters we can vary:

* length of rotor blades (`radius_rotor`) - 60 m versus 33 m
  + determines area of wind turbine (`area_rotor` as `pi * radius_rotor^2`)
* proportion of area covered by acoustic monitoring (`proportion_covered`)
  + determines area of acoustic monitoring (`area_monitored` as `area_rotor * proportion_covered`)
  + determines radius to detect bars (`radius_monitored` as `sqrt(area_monitored / pi)`)
* number of bats simulated (`n`)
  + could be either total (for now) or number monitored (maybe later)


## Simulated Data

```{r load.simulated-data}
scenarios <- 
  read_rds(here("output", "data-proc", "simulation-runs-norm.rds")) %>% 
  ## remove extremely skewed distributions
  filter(!str_detect(distribution, "_5$")) %>% 
  ## remove outdated 23% scenario
  filter(prop_monitored != .23) %>% 
  group_by(n, prop_monitored, distribution) %>% 
  mutate(diff = prop_monitored - median(prop_n_monitored)) %>% 
  ungroup() %>% 
  mutate(
    distribution = factor(
      distribution, 
      levels = c(
        "uniform", "random", 
        "inner_1", "inner_3",
        "outer_1", "outer_3", 
        "bottom_1", "bottom_3", 
        "top_1", "top_3"
      ), 
      labels = c(
        "a) uniform", "b) random",
        "c) inner — weak", "d) inner — strong",
        "e) outer — weak", "f) outer — strong",
        "g) bottom — weak", "h) bottom — strong",
        "i) top — weak", "j) top — strong"
      )
    ),
    prop_monitored_lab = paste0(prop_monitored * 100, "%"),
    prop_monitored_lab = fct_reorder(prop_monitored_lab, prop_monitored)
  )
```


## Visualizations Bat Passes

### Error Bars Deviation Bat Passes Recorded vs. Expected

Distribution (col) x Monitored Area (color) x Passes (x)

```{r lineplot-outcomes-summary, fig.width=13.5, fig.height=7.3}
scenarios %>% 
  group_by(distribution, prop_monitored, n) %>% 
  summarize(mean = mean(prop_n_monitored), sd = sd(prop_n_monitored)) %>% 
  ungroup() %>% 
  mutate(
    base = mean - prop_monitored,
    min = base - sd, 
    max = base + sd
  ) %>% 
  ggplot(aes(factor(n), base, color = prop_monitored, group = prop_monitored)) +
  geom_hline(aes(yintercept = 0), color = "grey75", size = 1.2)  + 
  geom_line(
    aes(color = prop_monitored, 
        color = after_scale(colorspace::desaturate(colorspace::lighten(color, .6), .4))),
    size = .7, show.legend = FALSE
  ) +
  geom_pointrange(aes(ymin = min, ymax = max), size = .5) +
  facet_wrap(~distribution, nrow = 2, dir = "v") +
  scale_x_discrete(expand = c(.05, .05)) +
  scale_y_continuous(expand = c(.012, .012), breaks = -5:5 / 10) +
  # scico::scale_color_scico(
  #   palette = "bamako", end = .85, direction = -1, name = "Proportion\ncovered\nby AUD:",
  #   breaks = c(.04, seq(.05, .5, by = .05)), labels = scales::percent_format(accuracy = 1)
  # ) +
  # scale_color_viridis_c(
  #   option = "turbo", name = "Proportion\ncovered\nby AUD:",
  #   breaks = c(.04, seq(.05, .5, by = .05)), labels = scales::percent_format(accuracy = 1)
  # ) +
  scico::scale_color_scico(
    palette = "hawai", end = .85, direction = -1, name = "Proportion\ncovered\nby AUD:",
    breaks = c(.04, seq(.05, .5, by = .05)), labels = scales::percent_format(accuracy = 1)
  ) +
  guides(color = guide_legend(keywidth = unit(.6, "lines"), keyheight = unit(1.2, "lines"))) +
  labs(x = "Number of bat passes (categorical axes)", y = "Deviation from expected proportion") +
  theme(panel.spacing.x = unit(.8, "lines"), axis.text = element_text(size = 10),
        legend.text = element_text(hjust = 1))

ggsave(here("plots", "fig3_passes_recorded_mean_sd_lines_cat_alt2.pdf"), 
       width = 13.5, height = 7.3, device = cairo_pdf)
ggsave(here("plots", "fig3_passes_recorded_mean_sd_lines_cat_alt2.png"), 
       width = 13.5, height = 7.3, dpi = 800)

## continuous x axis
# scenarios %>% 
#   group_by(distribution, prop_monitored, n) %>% 
#   summarize(mean = mean(prop_n_monitored), sd = sd(prop_n_monitored)) %>% 
#   ungroup() %>% 
#   mutate(
#     base = mean - prop_monitored,
#     min = base - sd, 
#     max = base + sd
#   ) %>% 
#   ggplot(aes(n, base, color = prop_monitored, group = prop_monitored)) +
#   geom_hline(aes(yintercept = 0), color = "grey75", size = 1.2)  + 
#   geom_line(
#     aes(color = prop_monitored, 
#         color = after_scale(colorspace::desaturate(colorspace::lighten(color, .6), .4))),
#     size = .7, show.legend = FALSE
#   ) +
#   geom_pointrange(aes(ymin = min, ymax = max), size = .4) +
#   facet_wrap(~distribution, nrow = 2, dir = "v") +
#   scale_x_continuous(expand = c(.04, .04), breaks = unique(scenarios$n),
#                      guide = guide_axis(n.dodge = 2)) +
#   scale_y_continuous(expand = c(.012, .012), breaks = -5:5 / 10) +
#   scico::scale_color_scico(
#     palette = "bamako", end = .8, direction = -1, name = "Proportion\ncovered\nby AUD:",
#     breaks = seq(.05, .5, by = .05), labels = scales::percent_format(accuracy = 1)
#   ) +
#   guides(color = guide_legend(keywidth = unit(.6, "lines"), keyheight = unit(1.2, "lines"))) +
#   labs(x = "Number of bat passes", y = "Deviation from expected proportion") +
#   theme(panel.spacing.x = unit(.6, "lines"), 
#         axis.text.x = element_text(size = 9),
#         axis.text.y = element_text(size = 12),
#         legend.text = element_text(hjust = 1))
# 
# ggsave(here("plots", "figX_passes_recorded_mean_sd_lines_cont.pdf"), 
#        width = 17, height = 8.5, device = cairo_pdf)
# ggsave(here("plots", "figX_passes_recorded_mean_sd_lines_cont.png"), 
#        width = 17, height = 8.5, dpi = 800)
```


### Boxplots Relative Difference Predicted vs. Expected

#### Dedicated Scenarios

```{r boxplot-passes-difference-scenarios, fig.width=12, fig.height=9}
colors <- scico::scico(n = 9, palette = "roma")[c(8,2)]

data_rel_scen <- 
  scenarios %>%
  filter((n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5)) %>% 
  mutate(
    diff_passes = ((n_monitored / prop_monitored) - n) / n,
    scenario = if_else(prop_monitored == .04, "Low", "High")
  ) %>% 
  bind_rows(
    tibble(
      distribution = factor("a) uniform", levels = levels(scenarios$distribution)),
      label = c("Overestimation", "Underestimation"),
      scenario = "High",
      diff_passes = c(1.25, -.75),
      color = colors
    )
  )

data_rel_scen %>% 
  filter(is.na(label)) %>% 
  ggplot(aes(scenario, diff_passes)) +
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = 0, ymax = Inf, fill = colors[1], alpha = .12) + 
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, fill = colors[2], alpha = .12) + 
  geom_text(data = data_rel_scen, aes(label = label, color = color), hjust = .15, fontface = "bold", size = 5) +
  geom_hline(yintercept = 0, size = .6, linetype = "31", color = "grey75") +
  geom_boxplot(color = "grey45", size = .6, width = .5, 
               position = position_nudge(x = .05), 
               outlier.size = .9, outlier.shape = 1) +
  geom_point(color = "grey90", shape = "-", size = 10, 
             position = position_nudge(x = -.31)) +
  geom_point(color = "grey45", shape = "-", size = 10, alpha = .05, 
             position = position_nudge(x = -.31)) +
  stat_summary(geom = "point", shape = 18, size = 4.5, color = "#212121", 
               position = position_nudge(x = .05)) +
  facet_wrap(~distribution, nrow = 2, dir = "v") + 
  scale_y_continuous(expand = c(.04, .04), breaks = seq(-1, 3.5, by = .5)) +
  scale_color_identity() +
  labs(x = "Coverage scenario",
       y = "Relative difference of predicted versus expected bat passes") +
  theme(axis.text.x = element_text(size = 13))

ggsave(here("plots", "fig4_passes_difference_boxplots_rel_scenarios.pdf"), 
       width = 12, height = 7.7, device = cairo_pdf)
ggsave(here("plots", "fig4_passes_difference_boxplots_rel_scenarios.png"), 
       width = 12, height = 7.7, dpi = 800)
```


#### All Scenarios with 400 Bat Passes

```{r boxplot-passes-difference-grid-relative, fig.width=12, fig.height=9}
data_rel <- 
  scenarios %>%
  filter(n == 400) %>% 
  filter(!prop_monitored == .04) %>% ## remove dedicated scenario
  mutate(diff_passes = ((n_monitored / prop_monitored) - n) / n) %>% 
  bind_rows(
    tibble(
      distribution = factor("a) uniform", levels = levels(scenarios$distribution)),
      label = c("Overestimation", "Underestimation"),
      prop_monitored_lab = factor("10%", levels = levels(scenarios$prop_monitored_lab)),
      diff_passes = c(1.25, -.67),
      color = colors
    )
  )

data_rel %>% 
  filter(is.na(label)) %>% 
  ggplot(aes(prop_monitored_lab, diff_passes)) +
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = 0, ymax = Inf, fill = colors[1], alpha = .12) + 
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, fill = colors[2], alpha = .12) + 
  geom_text(data = data_rel, aes(label = label, color = color), hjust = 0, fontface = "bold", size = 6) +
  geom_hline(yintercept = 0, size = .6, linetype = "31", color = "grey75") +
  geom_boxplot(color = "grey45", width = .85, size = .5, 
               outlier.size = .8, outlier.alpha = .4, outlier.shape = 1) +
  stat_summary(geom = "point", shape = 18, size = 3, color = "#212121") +
  facet_wrap(~distribution, nrow = 2, dir = "v") + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(expand = c(.03, .03), breaks = seq(-1, 3.5, by = .5)) +
  scale_color_identity() +
  labs(x = "Area covered by AUD",
       y = "Relative difference of predicted versus expected bat passes") +
  theme(axis.text.x = element_text(size = 11))

ggsave(here("plots", "figS3_passes_difference_boxplots_rel.pdf"), 
       width = 15, height = 8.2, device = cairo_pdf)
ggsave(here("plots", "figS3_passes_difference_boxplots_rel.png"), 
       width = 15, height = 8.2, dpi = 800)
```


## Visualizations Fatalities

```{r fit-models}
fits_scenarios <- 
  scenarios %>% 
  mutate(n_expected = ifelse(n_monitored == 0, 0, n_monitored / prop_monitored)) %>% 
  nest(data = -c(distribution, prop_monitored, prop_monitored_lab)) %>% 
  mutate(
    fit = map(data, ~ lm(n_fatalities ~ n_expected , data = .x)),
    tidied = map(fit, tidy),
    glance = map(fit, glance),
    augment = map(fit, augment),
    rsq = glance %>% map_dbl('r.squared'),
    slope = tidied %>% map_dbl(function(x) x$estimate[2]),
    se = tidied %>% map_dbl(function(x) x$std.error[2])
  ) %>% 
  dplyr::select(distribution, prop_monitored, prop_monitored_lab, rsq, slope, se) %>% 
  mutate(
    t = (.01 - slope) / se, ## t value = (expected slope - observed slope) / standard error
    p = 2*pt(abs(t), 1200-2, lower.tail = FALSE) ## p-value = two-tailed test of t value and d.f. (n - 2)
  )
```

### Regression Fatalities vs Predicted Bat Passes — What we observe

#### Dedicated Scenarios

##### Low-Coverage Scenario

```{r plots-fatalities-passes-monitored-low-coverage, fig.width=14, fig.height=7.5}
p_data_low <- 
  scenarios %>% 
  filter(prop_monitored == .04) %>% 
  mutate(n_expected = ifelse(n_monitored == 0, 0, n_monitored / prop_monitored))

p_data_low %>% 
  left_join(fits_scenarios) %>% 
  ggplot(aes(n_expected, n_fatalities)) +
  geom_abline(intercept = 0, slope = .01, color = "grey45", linetype = "31", size = .4) +
  geom_point(shape = 16, alpha = .08) +
  geom_quantile(quantiles = c(0.25, 0.75), color = "#D89684", alpha = .7, size = .6) +
  geom_quantile(quantiles = c(0.5), color = "#E60000", size = .9) +
  # geom_text(
  #   aes(label = paste("R² = ", sprintf("%1.2f", rsq)), 
  #       x = 0, y = 87), 
  #   stat = "unique", family = "Open Sans", color = "grey30",
  #   size = 3.7, hjust = 0
  # ) +
  facet_wrap(~ distribution, nrow = 2, scales = "free_x", dir = "v") +
  scale_x_continuous(breaks = 0:5*4000, limits = c(NA, max(p_data_low$n_expected)),
                     labels = scales::comma_format()) +
  scale_y_continuous(breaks = 0:4*20) +
  labs(title = "Low coverage scenarios",
       subtitle = "4% acoustic monitoring area",
       x = "Number of bat passes (predicted)", y = "Number of fatalities (simulated)") + 
  theme(
    panel.grid.major.y = element_blank(), 
    panel.spacing.x = unit(1.2, "lines"), 
    panel.spacing.y = unit(.6, "lines"), 
    legend.text = element_text(hjust = 1),
    strip.text = element_text(hjust = 0),
    plot.subtitle = element_text(margin = margin(t = 0, b = 20))
  )

ggsave(here("plots", "fig5_fatalities_correlation_low_coverage.pdf"), 
       width = 14, height = 7.5, device = cairo_pdf)

ggsave(here("plots", "fig5_fatalities_correlation_low_coverage.png"), 
       width = 14, height = 7.5, dpi = 800)
```

#### High-Coverage Scenario

```{r plots-fatalities-passes-monitored-high-coverage, fig.width=14, fig.height=7.5}
p_data_high <- 
  scenarios %>% 
  filter(prop_monitored == .5) %>% 
  mutate(n_expected = ifelse(n_monitored == 0, 0, n_monitored / prop_monitored))

p_data_high %>% 
  left_join(fits_scenarios) %>% 
  ggplot(aes(n_expected, n_fatalities)) +
  geom_abline(intercept = 0, slope = .01, color = "grey45", linetype = "31", size = .4) +
  geom_point(shape = 16, alpha = .08) +
  geom_quantile(quantiles = c(0.25, 0.75), color = "#D89684", alpha = .7, size = .6) +
  geom_quantile(quantiles = c(0.5), color = "#E60000", size = .9) +
  # geom_text(
  #   aes(label = paste("R² = ", sprintf("%1.2f", rsq)), 
  #       x = 0, y = 87), 
  #   stat = "unique", family = "Open Sans", color = "grey30",
  #   size = 3.7, hjust = 0
  # ) +
  facet_wrap(~ distribution, nrow = 2, scales = "free_x", dir = "v") +
  scale_x_continuous(breaks = 0:5*2000, limits = c(NA, max(p_data_high$n_expected)),
                     labels = scales::comma_format()) +
  scale_y_continuous(breaks = 0:4*20) +
  labs(title = "High coverage scenarios",
       subtitle = "50% acoustic monitoring",
       x = "Number of bat passes (predicted)", y = "Number of fatalities (simulated)") + 
  theme(
    panel.grid.major.y = element_blank(), 
    panel.spacing.x = unit(1.2, "lines"), 
    panel.spacing.y = unit(.6, "lines"), 
    legend.text = element_text(hjust = 1),
    strip.text = element_text(hjust = 0),
    plot.subtitle = element_text(margin = margin(t = 0, b = 20))
  )

ggsave(here("plots", "fig6_fatalities_correlation_high_coverage.pdf"), 
       width = 14, height = 7.5, device = cairo_pdf)

ggsave(here("plots", "fig6_fatalities_correlation_high_coverage.png"), 
       width = 14, height = 7.5, dpi = 800)
```


#### All Scenarios with 400 Bat Passes

```{r plots-fatalities-passes-monitored-all, fig.width=14, fig.height=7.5}
p_data_all <- scenarios %>% 
  mutate(n_expected = ifelse(n_monitored == 0, 0, n_monitored / prop_monitored)) 

p_data_all %>% 
  ggplot(aes(n_expected, n_fatalities)) +
  geom_abline(intercept = 0, slope = .01, color = "grey45", linetype = "31", size = .4) +
  geom_point(shape = 16, alpha = .08) +
  geom_quantile(quantiles = c(0.25, 0.75), color = "#D89684", alpha = .7, size = .6) +
  geom_quantile(quantiles = c(0.5), color = "#E60000", size = .9) +
  # geom_text(
  #   aes(label = paste("R² = ", sprintf("%1.2f", rsq)), 
  #       x = 0, y = 87), 
  #   stat = "unique", family = "Open Sans", color = "grey30",
  #   size = 3.7, hjust = 0
  # ) +
  facet_grid(prop_monitored_lab ~ distribution, scales = "free_x") +
  scale_x_continuous(breaks = 0:5*4000, limits = c(NA, max(p_data_all$n_expected)),
                     labels = scales::comma_format()) +
  scale_y_continuous(breaks = 0:4*20) +
  labs(x = "Number of bat passes (predicted)", y = "Number of fatalities (simulated)") + 
  theme(
    panel.grid.major.y = element_blank(), 
    panel.spacing = unit(.8, "lines"), 
    legend.text = element_text(hjust = 1),
    strip.text.x = element_text(hjust = 0),
    strip.text.y = element_text(angle = 0, hjust = 1, margin = margin(3, 9, 3, 9))
  ) -> d

ggsave(here("plots", "figS4_fatalities_correlation_all.pdf"), 
       width = 24, height = 15, device = cairo_pdf)

ggsave(here("plots", "figS4_fatalities_correlation_all.png"), 
       width = 24, height = 15, dpi = 800)
```


### p-Values Slopes

```{r plot-slope-pvalue}
fits_scenarios %>% 
  ggplot(aes(prop_monitored_lab, fct_rev(distribution))) +
  #geom_tile(aes(fill = base), color = "white", size = .7) +
  geom_tile(aes(fill = p), color = "white", size = .8) +
  geom_text(
    aes(label = sprintf("%1.2f", p), color = p < .05),
    family = "Open Sans", size = 4.5
  ) +
  coord_cartesian(expand = FALSE, clip = "off") +
  scale_color_manual(values = c("#fefefe", "#212121"), guide = "none") +
  scale_x_discrete(position = "top") +
  # scico::scale_fill_scico(
  #   palette = "batlowW", direction = -1, name = "P-value (t-test, df = 1.198)",
  #   begin = .12, breaks = seq(0, 1, by = .1), midpoint = .05, limits = c(0, 1)
  # ) +
  scico::scale_fill_scico(
    palette = "batlowW", direction = -1, end = .85, 
    name = "P-value (t-test, df = 1,198)", limits = c(0, 1),
    breaks = seq(0, 1, by = .1), labels = function(x) sprintf("%1.1f", x)
  ) +
  scale_alpha_manual(values = c(0, 1), guide = "none") +
  scale_alpha_manual(values = c(0, 1), guide = "none") +
  guides(fill = guide_colorsteps(title.position = "top", show.limits = TRUE)) +
  labs(x = "Proportion covered by AUD", y = NULL) +
  theme(panel.spacing = unit(.9, "lines"), 
        panel.background = element_rect(size = .7, color = "white", fill = "transparent"),
        panel.border = element_rect(color = "transparent", fill = "transparent"),
        axis.title.x.top = element_text(face = "bold", margin = margin(t = 8, b = 12)),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14, face = "bold", hjust = 0),
        axis.ticks = element_line(color = "transparent"),
        axis.ticks.length = unit(.3, "lines"),
        legend.position = "top",
        legend.justification = "left",
        legend.key.width = unit(6, "lines"), legend.key.height = unit(.6, "lines"))

ggsave(here("plots", "tab1_slopes_ttest_heatmap.pdf"), 
       width = 12, height = 6.7, device = cairo_pdf)
ggsave(here("plots", "tab1_slopes_ttest_heatmap.png"), 
       width = 12, height = 6.7, dpi = 800)
```


## Additional Visualizations

### Heatmap Deviation Bat Passes Recorded vs. Expected

```{r heatmap-outcomes-summary, fig.width=14.5, fig.height=8.7, include=FALSE, eval=FALSE}
scenarios %>% 
  group_by(distribution, prop_monitored, prop_monitored_lab, n) %>% 
  summarize(mean = mean(prop_n_monitored), sd = sd(prop_n_monitored)) %>% 
  ungroup() %>% 
  mutate(
    base = mean - prop_monitored,
    scenario_highlight = ifelse(
      (n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5), "1", "0"
    ),
    label_highlight = ifelse(
      (n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5), 
      sprintf("%1.3f", base), NA_character_
    )
  ) %>% 
  ggplot(aes(factor(n), fct_rev(prop_monitored_lab))) +
  geom_tile(aes(fill = base), color = "white", size = .7) +
  geom_tile(aes(color = scenario_highlight), fill = "transparent", size = .8) +
  geom_text(
    aes(label = label_highlight), 
    color = "white", family = "Open Sans", size = 3.3, fontface = "bold"
  ) +
  geom_text(
    aes(label = label_highlight, alpha = abs(base) < .2), 
    color = "#212121", family = "Open Sans", size = 3.3, fontface = "bold"
  ) +
  facet_wrap(~distribution, nrow = 2, dir = "v") +
  coord_cartesian(expand = FALSE, clip = "off") +
  scale_color_manual(values = c("transparent", "#212121"), guide = "none") +
  scico::scale_fill_scico(
    palette = "roma", direction = 1, name = "Deviation from expected proportion",
    breaks = seq(-.5, .5, by = .1), midpoint = 0
  ) +
  scale_alpha_manual(values = c(0, 1), guide = "none") +
  guides(fill = guide_colorsteps(title.position = "top")) +
  labs(x = "Number of bat passes", y = "Proportion covered by AUD") +
  theme(panel.spacing = unit(.9, "lines"), 
        panel.background = element_rect(size = .7, color = "white", fill = "transparent"),
        panel.border = element_rect(color = "transparent", fill = "transparent"),
        axis.text = element_text(size = 11.5),
        axis.ticks = element_line(color = "transparent"),
        axis.ticks.length = unit(.3, "lines"),
        strip.text = element_text(color = "black"),
        strip.background = element_rect(color = "transparent", fill = "transparent"),
        legend.position = "top",
        legend.justification = "left",
        legend.key.width = unit(6, "lines"), legend.key.height = unit(.6, "lines"))

ggsave(here("plots", "bat_passes", "passes_recorded_mean_heatmap_horizontal.pdf"), width = 14.5, height = 8.7, device = cairo_pdf)
```

```{r heatmap-outcomes-summary-vertical, fig.width=13.5, fig.height=5.5, include=FALSE, eval=FALSE}
scenarios %>% 
  group_by(distribution, prop_monitored, prop_monitored_lab, n) %>% 
  summarize(mean = mean(prop_n_monitored), sd = sd(prop_n_monitored)) %>% 
  ungroup() %>% 
  mutate(
    base = mean - prop_monitored,
    scenario_highlight = ifelse(
      (n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5), "1", "0"
    ),
    label_highlight = ifelse(
      (n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5), 
      sprintf("%1.3f", base), NA_character_
    )
  ) %>% 
  ggplot(aes(prop_monitored_lab, fct_rev(factor(n)))) +
  geom_tile(aes(fill = base), color = "white", size = .7) +
  geom_tile(aes(color = scenario_highlight), fill = "transparent", size = .8) +
  geom_text(
    aes(label = label_highlight), 
    color = "white", family = "Open Sans", size = 3.3, fontface = "bold"
  ) +
  geom_text(
    aes(label = label_highlight, alpha = abs(base) < .2), 
    color = "#212121", family = "Open Sans", size = 3.3, fontface = "bold"
  ) +
  facet_wrap(~distribution, ncol = 2, dir = "h") +
  coord_cartesian(expand = FALSE, clip = "off") +
  scale_color_manual(values = c("transparent", "#212121"), guide = "none") +
  scico::scale_fill_scico(
    palette = "roma", direction = 1, name = "Deviation from expected proportion",
    breaks = seq(-.5, .5, by = .1), midpoint = 0
  ) +
  scale_alpha_manual(values = c(0, 1), guide = "none") +
  guides(fill = guide_colorsteps(title.position = "top")) +
  labs(x = "Proportion covered by AUD", y = "Number of bat passes") +
  theme(panel.spacing = unit(.9, "lines"), 
        panel.background = element_rect(size = .7, color = "white", fill = "transparent"),
        panel.border = element_rect(color = "transparent", fill = "transparent"),
        axis.text = element_text(size = 11.5),
        axis.ticks = element_line(color = "transparent"),
        axis.ticks.length = unit(.3, "lines"),
        strip.text = element_text(color = "black"),
        strip.background = element_rect(color = "transparent", fill = "transparent"),
        legend.position = "top",
        legend.justification = "left",
        legend.key.width = unit(6, "lines"), legend.key.height = unit(.6, "lines"))

ggsave(here("plots", "bat_passes", "passes_recorded_mean_heatmap_vertical.pdf"), width = 12, height = 13.2, device = cairo_pdf)
```


### Boxplots Proportion of Passes Monitored

```{r boxplots-passes-monitored-grid, fig.width=23, fig.height=13}
box <- 
  ggplot(scenarios, aes(factor(n), prop_n_monitored)) +
  geom_hline(aes(yintercept = prop_monitored), color = "grey75", size = .7)  + 
  geom_boxplot(aes(color = diff), size = .4, outlier.shape = 1, outlier.size = .3) + 
  scale_y_continuous(labels = scales::percent_format(), 
                     sec.axis = dup_axis(name = "Area covered by AUD", breaks = NULL, labels = NULL)) +
  scale_color_gradient2(low = "firebrick", mid = "grey40", high = "firebrick", 
                        limits = c(-.5, .5), guide = "none") +
  labs(x = "Number of bat passes", y = "Proportion of passes monitored") +
  theme(panel.spacing.y = unit(.65, "lines"), axis.text = element_text(size = 9),
        axis.title.x = element_text(size = 18, face = "bold"), 
        axis.title.y = element_text(size = 18, face = "bold"), 
        strip.text.x = element_text(size = 18),
        strip.text.y = element_text(size = 16),
        axis.title.y.right = element_text(size = 21, color = "grey60", face = "bold", margin = margin(l = 12)))

## fixed y scale
box + facet_grid(prop_monitored_lab ~ distribution)

ggsave(here("plots", "bat_passes", "passes_recorded_boxplots_fixed.pdf"), 
       width = 23, height = 13, device = cairo_pdf)
ggsave(here("plots", "bat_passes", "passes_recorded_boxplots_fixed.png"), 
       width = 23, height = 13, dpi = 800)

## free y scale
box + facet_grid(prop_monitored_lab ~ distribution, scale = "free_y") 

ggsave(here("plots", "bat_passes", "passes_recorded_boxplots_free.pdf"), 
       width = 23, height = 13, device = cairo_pdf)
ggsave(here("plots", "bat_passes", "passes_recorded_boxplots_free.png"), 
       width = 23, height = 13, dpi = 800)
```


### Boxplots Absolute Difference Predicted vs. Expected

#### for dedicated scenarios

```{r boxplot-passes-difference-scenarios-absolute, fig.width=12, fig.height=9}
data_abs_scen <- 
  scenarios %>% 
  filter((n == 400 & prop_monitored == .04) | (n == 100 & prop_monitored == .5)) %>% 
  mutate(
    diff_passes = (n_monitored / prop_monitored) - n,
    scenario = if_else(prop_monitored == .04, "Low", "High")
  ) %>% 
  bind_rows(
    tibble(
      distribution = factor("a) uniform", levels = levels(scenarios$distribution)),
      label = c("Overestimation", "Underestimation"),
      scenario = "High",
      diff_passes = c(625, -250),
      color = colors
    )
  )
  
data_abs_scen %>%
  filter(is.na(label)) %>% 
  ggplot(aes(scenario, diff_passes)) +
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = 0, ymax = Inf, fill = colors[1], alpha = .12) + 
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, fill = colors[2], alpha = .12) + 
  geom_text(data = data_abs_scen, aes(label = label, color = color), hjust = .15, fontface = "bold", size = 5) +
  geom_hline(yintercept = 0, size = .6, linetype = "31", color = "grey75") +
  geom_boxplot(color = "grey45", size = .6, width = .5, 
               position = position_nudge(x = .05), 
               outlier.size = .9, outlier.shape = 1) +
  geom_point(color = "grey90", shape = "-", size = 10.1, 
             position = position_nudge(x = -.31)) +
  geom_point(color = "grey45", shape = "-", size = 10.1, alpha = .05, 
             position = position_nudge(x = -.31)) +
  stat_summary(geom = "point", shape = 18, size = 4.5, color = "#212121", 
               position = position_nudge(x = .05)) +
  facet_wrap(~distribution, nrow = 2, dir = "v") + 
  scale_y_continuous(expand = c(.04, .04), breaks = seq(-800, 1600, by = 400)) +
  scale_color_identity() +
  labs(x = "Coverage scenario",
       y = "Absolute difference of predicted versus expected bat passes") +
  theme(axis.text.x = element_text(size = 13))

ggsave(here("plots", "bat_passes", "passes_difference_boxplots_abs_scenarios.pdf"), 
       width = 12, height = 7.7, device = cairo_pdf)
ggsave(here("plots", "bat_passes", "passes_difference_boxplots_abs_scenarios.png"), 
       width = 12, height = 7.7, dpi = 800)
```


#### All Scenarios with 400 Bat Passes

```{r boxplot-passes-difference-grid-absolute, fig.width=12, fig.height=9}
## absolute
data_abs <- 
  scenarios %>%
  filter(n == 400) %>% 
  filter(!prop_monitored == .04) %>% ## remove dedicated scenario 
  mutate(diff_passes = (n_monitored / prop_monitored) - n) %>% 
  bind_rows(
    tibble(
      distribution = factor("a) uniform", levels = levels(scenarios$distribution)),
      label = c("Overestimation", "Underestimation"),
      prop_monitored_lab = factor("10%", levels = levels(scenarios$prop_monitored_lab)), 
      diff_passes = c(625, -250),
      color = colors
    )
  )

data_abs %>% 
  filter(is.na(label)) %>% 
  ggplot(aes(prop_monitored_lab, diff_passes)) +
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = 0, ymax = Inf, fill = colors[1], alpha = .12) + 
  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, fill = colors[2], alpha = .12) + 
  geom_text(data = data_abs, aes(label = label, color = color), hjust = 0, fontface = "bold", size = 6) +
  geom_hline(yintercept = 0, size = .6, linetype = "31", color = "grey75") +
  geom_boxplot(color = "grey45", width = .85, size = .5, 
               outlier.size = .8, outlier.alpha = .4, outlier.shape = 1) +
  stat_summary(geom = "point", shape = 18, size = 3, color = "#212121") +
  facet_wrap(~distribution, nrow = 2, dir = "v") + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(expand = c(.03, .03), breaks = seq(-800, 1600, by = 400)) +
  scale_color_identity() +
  labs(x = "Area covered by AUD",
       y = "Absolute difference of predicted versus expected bat passes") +
  theme(axis.text.x = element_text(size = 11))

ggsave(here("plots", "bat_passes", "passes_difference_boxplots_abs.pdf"), 
       width = 15, height = 8.2, device = cairo_pdf)
ggsave(here("plots", "bat_passes", "passes_difference_boxplots_abs.png"), 
       width = 15, height = 8.2, dpi = 800)
```


### Regression Fatalities vs Predicted Bat Passes — What really happens

```{r plots-fatalities-passes-reality, fig.width=13.5, fig.height=3.2}
## with variation
scenarios %>% 
  filter(prop_monitored == .05) %>% 
  ggplot(aes(n, n_fatalities)) +
  #geom_abline(slope = .01, intercept = 0, size = .6, color = "grey75") +
  geom_jitter(alpha = .02, width = 20, height = 0) +
  geom_quantile(quantiles = c(.25, .75), color = "dodgerblue3", size = .6) +
  geom_quantile(quantiles = c(.5), color = "red", size = .9) +
  facet_grid(~ distribution) +
  scale_x_continuous(expand = c(.1, .1)) +
  labs(x = "Number of bat passes (reality)",
       y = "Number of fatalities") +
  theme(panel.grid.major.y = element_blank(), axis.text.x = element_text(size = 10))

ggsave(here("plots", "fatalities", "fatalities_correlation_reality_var.pdf"), 
       width = 13.5, height = 3.2, device = cairo_pdf)
ggsave(here("plots", "fatalities", "fatalities_correlation_reality_var.png"), 
       width = 13.5, height = 3.2, dpi = 800)


## without variation
# scenarios %>% 
#   filter(prop_monitored == .05) %>% 
#   mutate(n_fatalities = round(n / 100)) %>% 
#   ggplot(aes(n, n_fatalities)) +
#   #geom_abline(slope = .01, intercept = 0, size = .6, color = "grey75") +
#   geom_point(alpha = .02) +
#   geom_quantile(quantiles = c(0.25, 0.75), color = "dodgerblue3", size = .6) +
#   geom_quantile(quantiles = c(0.5), color = "red", size = .9) +
#   facet_grid(~ distribution) +
#   scale_x_continuous(expand = c(.1, .1)) +
#   labs(x = "Number of bat passes (reality)",
#        y = "Number of fatalities") + #,
#        #title = "What really happens",
#        #subtitle = "Number of fatalities per number of bat passes (1% correlation without variation)") +
#   theme(panel.grid.major.y = element_blank(), axis.text.x = element_text(size = 10))
# 
# ggsave(here("plots", "fig_Sx_fatalities_correlation_reality_fix.pdf"), 
#        width = 13.5, height = 3.2, device = cairo_pdf)
# ggsave(here("plots", "fig_Sx_fatalities_correlation_reality_fix.png"), 
#        width = 13.5, height = 3.2, dpi = 800)
```

***

<details><summary>Session Info</summary>

```{r sessionInfo}
Sys.time()
sessionInfo()
```

</details>
